
# CL & CE

The following analysis checks whether landings have corresponding effort. This is done by merging the CE and CL datasets using the key fields: vessel flag country, year, quarter, month, area, statistical rectangle, fisheries management unit, GSA subarea, jurisdiction area, fishing area category, fresh water name, EEZ, national fishing activity, metier 6, incidental by-catch mitigation device, location, vessel length category, fishing technique, mesh size range, supra region, geographical indicator, specific conditions to technical measures, and deep sea regulation.

```{r clce-key-columns}
CEkeyColumns <- c(
  "CErecType", "CEvesFlagCou", "CEyear", "CEquar", "CEmonth",
  "CEarea", "CEstatRect", "CEfishManUnit", "CEgsaSubarea",
  "CEjurisdArea", "CEfishAreaCat", "CEfreshWatNam", "CEeconZone",
  "CEnatFishAct", "CEmetier6", "CEIBmitiDev", "CEloc",
  "CEvesLenCat", "CEfishTech", "CEmesSizRan", "CEsupReg",
  "CEgeoInd", "CEspeConTech", "CEdeepSeaReg"
)

CLkeyColumns <- c(
  "CLrecType", "CLvesFlagCou", "CLyear", "CLquar", "CLmonth",
  "CLarea", "CLstatRect", "CLfishManUnit", "CLgsaSubarea",
  "CLjurisdArea", "CLfishAreaCat", "CLfreshWatNam", "CLeconZone",
  "CLnatFishAct", "CLmetier6", "CLIBmitiDev", "CLloc",
  "CLvesLenCat", "CLfishTech", "CLmesSizRan", "CLsupReg",
  "CLgeoInd", "CLspeConTech", "CLdeepSeaReg"
)
```

## Number of unique keys in CE and CL datasets

```{r clce-unique-keys}
CEkeys <- CE %>%
  group_by(across(all_of(CEkeyColumns))) %>%
  summarise(
    CEsciDaySea  = sum(CEsciDaySea,  na.rm = TRUE),
    CEsciFishDay = sum(CEsciFishDay, na.rm = TRUE),
    .groups = "drop"
  )
colnames(CEkeys) <- sub("^CE", "", colnames(CEkeys))

CLkeys <- CL %>%
  group_by(across(all_of(CLkeyColumns))) %>%
  summarise(CLsciWeight = sum(CLsciWeight, na.rm = TRUE), .groups = "drop")
colnames(CLkeys) <- sub("^CL", "", colnames(CLkeys))

# Join columns: the 23 shared spatial/temporal/metier key fields.
# "recType" is intentionally excluded — its value is always "CE" vs "CL",
# so including it would make every join produce zero rows.
# Metric columns are also excluded.
non_join <- c("recType", "sciDaySea", "sciFishDay", "sciWeight")
join_cols <- intersect(
  setdiff(colnames(CEkeys), non_join),
  setdiff(colnames(CLkeys), non_join)
)
```

```{r clce-key-setdiff-check}
# Issue #13: warn about year mismatches before merging
cl_years_key <- sort(unique(CLkeys$year))
ce_years_key <- sort(unique(CEkeys$year))
missing_ce   <- setdiff(cl_years_key, ce_years_key)
missing_cl   <- setdiff(ce_years_key, cl_years_key)
if (length(missing_ce) > 0)
  message("Years in CL keys but not CE keys: ", paste(missing_ce, collapse = ", "))
if (length(missing_cl) > 0)
  message("Years in CE keys but not CL keys: ", paste(missing_cl, collapse = ", "))
```

```{r clce-key-plot}
# Add an explicit dataset label before stripping prefixes so the plot legend works
CEkeys_lab <- CEkeys %>% mutate(dataset = "CE")
CLkeys_lab <- CLkeys %>% mutate(dataset = "CL")

keysSummary <- bind_rows(CEkeys_lab, CLkeys_lab) %>%
  group_by(vesFlagCou, year, dataset) %>%
  summarise(n = n(), .groups = "drop")

if (nrow(keysSummary) > 0 && any(!is.na(keysSummary$vesFlagCou))) {
  print(
    ggplot(keysSummary, aes(year, n, fill = dataset)) +
      geom_bar(stat = "identity", position = "dodge") +
      facet_wrap(~ vesFlagCou, scales = "free_y") +
      RDBES_FILL +
      rdbes_theme() +
      labs(
        y     = "Number of unique keys",
        x     = "Year",
        fill  = "Dataset",
        title = "Comparison of CL and CE unique keys"
      )
  )
} else {
  message("No data to plot for CL/CE key comparison (keysSummary is empty or vesFlagCou is all NA).")
}
```

## Landings without corresponding effort

```{r clce-lan-no-effort, results='asis'}
lanWoEffort <- CLkeys %>%
  anti_join(CEkeys, by = join_cols)

rdbes_dt(lanWoEffort, caption = "Landings without corresponding effort", filter = "top")
```

## Tons per fishing day from merged CE and CL datasets

```{r clce-tons-per-day, results='asis'}
CECL <- CEkeys %>%
  inner_join(CLkeys, by = join_cols) %>%
  mutate(
    tonsPerFishingDay = sciWeight / sciFishDay,
    gearType          = substr(metier6, 1, 3)
  )

# Guard: facet_wrap crashes if the faceting variable has zero non-NA levels.
# This can happen when metier6 is entirely NA (gearType = NA after substr).
has_veslen  <- sum(!is.na(CECL$vesLenCat)) > 0
has_gear    <- sum(!is.na(CECL$gearType))  > 0

if (nrow(CECL) == 0) {
  message("No matching CL/CE keys — tons-per-fishing-day plots skipped.")
} else {
  if (has_veslen && has_gear) {
    print(
      CECL %>%
        ggplot(aes(gearType, tonsPerFishingDay)) +
        geom_boxplot(outlier.colour = "red3", fill = "#8da0cb", alpha = 0.7) +
        facet_wrap(~ vesLenCat, scales = "free") +
        rdbes_theme() +
        labs(y = "Tons per fishing day", x = "Gear type",
             title = "Tons per fishing day by gear and vessel length")
    )
    print(
      CECL %>%
        ggplot(aes(vesLenCat, tonsPerFishingDay)) +
        geom_boxplot(outlier.colour = "red3", fill = "#8da0cb", alpha = 0.7) +
        facet_wrap(~ gearType, scales = "free") +
        rdbes_theme() +
        labs(y = "Tons per fishing day", x = "Vessel length",
             title = "Tons per fishing day by vessel length and gear")
    )
  } else {
    message("vesLenCat or gearType contains only NA values — facet plots skipped.")
    print(
      CECL %>%
        ggplot(aes(tonsPerFishingDay)) +
        geom_histogram(bins = 30, fill = "#8da0cb", colour = "white") +
        rdbes_theme() +
        labs(x = "Tons per fishing day", title = "Distribution of tons per fishing day")
    )
  }
}
```
