
# Spatial checks

```{r spatial-setup, include=FALSE}
CE_DF <- CE
CL_DF <- CL
```

```{r spatial-functions, include=FALSE}

geom_ices_squares <- function(xlim = c(-49, 70), ylim = c(36, 85.5), ...) {
  outside <- FALSE
  if (xlim[1] < -49)  { xlim[1] <- -49;  outside <- TRUE }
  if (xlim[2] > 70)   { xlim[2] <- 70;   outside <- TRUE }
  if (ylim[1] < 36)   { ylim[1] <- 36;   outside <- TRUE }   # bug fix: was < -49
  if (ylim[2] > 85.5) { ylim[2] <- 85.5; outside <- TRUE }
  if (outside) message("Coordinates clamped to ICES rectangle extent [-49;70] x [36;85.5].")
  list(
    geom_vline(xintercept = seq(-49, 70), ...),
    geom_hline(yintercept = seq(36, 85.5, by = 0.5), ...),
    scale_x_continuous(sec.axis = sec_axis(
      ~ .x,
      breaks = seq(-49.5, 69.5, by = 1),
      labels = paste0(rep(LETTERS[1:12], each = 10), 0:9),
      guide  = guide_axis(check.overlap = TRUE)
    )),
    scale_y_continuous(sec.axis = sec_axis(
      ~ .x,
      breaks = seq(36.25, 85.25, by = 0.5),
      labels = sprintf("%02d", 1:99),
      guide  = guide_axis(check.overlap = TRUE)
    )),
    coord_quickmap(xlim, ylim)
  )
}
```

```{r spatial-top20, include=FALSE}
# Top 20 metiers by fishing days (CE)
top20_fd <- CE_DF %>%
  group_by(CEmetier6) %>%
  summarise(ofdTot = sum(CEoffFishDay, na.rm = TRUE), .groups = "drop") %>%
  slice_max(order_by = ofdTot, n = 20) %>%
  mutate(Top20metiers = "X")
CE_DF <- left_join(CE_DF, top20_fd, by = "CEmetier6") %>%
  mutate(topMetiers = if_else(is.na(Top20metiers), "OTH", CEmetier6))

# Top 20 metiers by landed value (CL)
top20_lv <- CL_DF %>%
  group_by(CLmetier6) %>%
  summarise(lvTot = sum(suppressWarnings(as.numeric(CLlanVal)), na.rm = TRUE),
            .groups = "drop") %>%
  slice_max(order_by = lvTot, n = 20) %>%
  mutate(Top20metiers = "X")
CL_DF <- left_join(CL_DF, top20_lv, by = "CLmetier6") %>%
  mutate(topMetiers = if_else(is.na(Top20metiers), "OTH", CLmetier6))

# Top 20 metiers by official weight (used for spatial maps — shared CL/CE classification)
top20_w <- CL_DF %>%
  group_by(CLmetier6) %>%
  summarise(wTot = sum(CLoffWeight, na.rm = TRUE), .groups = "drop") %>%
  slice_max(order_by = wTot, n = 20) %>%
  mutate(Top20metiersW = "X")

CL_DF <- left_join(CL_DF, top20_w, by = "CLmetier6") %>%
  mutate(topMetiersW = if_else(is.na(Top20metiersW), "OTH", CLmetier6))

CE_DF <- left_join(CE_DF, top20_w, by = c("CEmetier6" = "CLmetier6")) %>%
  mutate(topMetiersW = if_else(is.na(Top20metiersW), "OTH", CEmetier6))
```

## ICES rectangles and FAO areas

### CE

Area and ICES rectangle in the CE data (`CEarea`, `CEstatRect`) are compared with the ICES reference list area/rectangle relationship. The expected area for each rectangle is shown in `ICESAreaWithRectangle`. Note that `-9` is allowed as unknown rectangle.

```{r ce-rect-check, echo=FALSE, results='asis'}
ICESrect$sq_check <- "correct"

# Vectorised replacement for the row-by-row loop (faster & cleaner)
CE_sq <- CE_DF %>%
  filter(CEstatRect != "-9") %>%
  group_by(CEvesFlagCou, CEstatRect, CEarea) %>%
  summarise(t = n(), .groups = "drop") %>%
  left_join(ICESrect, by = c("CEarea" = "Area", "CEstatRect" = "ICESNAME")) %>%
  select(-any_of("Area_27"))

CE_wrong <- CE_sq %>%
  filter(is.na(sq_check)) %>%
  select(CEvesFlagCou, CEstatRect, CEarea) %>%
  left_join(select(ICESrect, ICESNAME, Area),
            by = c("CEstatRect" = "ICESNAME")) %>%
  distinct(CEvesFlagCou, CEstatRect, .keep_all = TRUE) %>%
  rename(ICESAreaWithRectangle = Area)

cat("\n\n**Overview of CE records with wrong/unexpected CEarea**\n\n")
rdbes_dt(CE_wrong, caption = "CE records with wrong/unexpected area", filter = "top")

cat("\n\n**CEid records with wrong/unexpected CEarea**\n\n")
cat("All CE records whose CEarea does not match the ICES reference list for that rectangle.\n\n")

# Vectorised semi_join replaces the row loop
CE_DF_wrong_areas <- CE_DF %>%
  semi_join(CE_wrong, by = c("CEvesFlagCou", "CEstatRect", "CEarea")) %>%
  select(CEid, CEvesFlagCou, CEyear, CEmonth, CEstatRect, CEarea,
         CEmetier6, CEvesLenCat, CEencrypVesIds)

rdbes_dt(CE_DF_wrong_areas, caption = "CE records with incorrect area (full detail)", filter = "top")
```

### CL

Area and ICES rectangle in the CL data (`CLarea`, `CLstatRect`) are compared with the ICES reference list. Note that `-9` is allowed as unknown rectangle.

```{r cl-rect-check, echo=FALSE, results='asis'}
ICESrect$sq_check <- "correct"

CL_sq <- CL_DF %>%
  filter(CLstatRect != "-9") %>%
  group_by(CLvesFlagCou, CLstatRect, CLarea) %>%
  summarise(t = n(), .groups = "drop") %>%
  left_join(ICESrect, by = c("CLarea" = "Area", "CLstatRect" = "ICESNAME")) %>%
  select(-any_of("Area_27"))

CL_wrong <- CL_sq %>%
  filter(is.na(sq_check)) %>%
  select(CLvesFlagCou, CLstatRect, CLarea) %>%
  left_join(select(ICESrect, ICESNAME, Area),
            by = c("CLstatRect" = "ICESNAME")) %>%
  distinct(CLvesFlagCou, CLstatRect, .keep_all = TRUE) %>%
  rename(ICESAreaWithRectangle = Area)

cat("\n\n**Overview of CL records with wrong/unexpected CLarea**\n\n")
rdbes_dt(CL_wrong, caption = "CL records with wrong/unexpected area", filter = "top")

cat("\n\n**CLid records with wrong/unexpected CLarea**\n\n")
cat("All CL records whose CLarea does not match the ICES reference list for that rectangle.\n\n")

CL_DF_wrong_areas <- CL_DF %>%
  semi_join(CL_wrong, by = c("CLvesFlagCou", "CLstatRect", "CLarea")) %>%
  select(CLid, CLvesFlagCou, CLyear, CLmonth, CLstatRect, CLarea,
         CLmetier6, CLvesLenCat, CLencrypVesIds)

rdbes_dt(CL_DF_wrong_areas, caption = "CL records with incorrect area (full detail)", filter = "top")
```

## ICES rectangle centroids (CL and CE) {.tabset}

CE and CL data points are plotted to ICES rectangle centroids. A third map shows CL records with no corresponding CE record. Note: `-9` (unknown rectangle) may legitimately produce such discrepancies.

```{r spatial-maps, include=FALSE, error=TRUE}
world <- ne_countries(scale = "medium", returnclass = "sf")
world <- st_set_crs(world, 4326)

map_combined    <- list()
CL_without_CE   <- list()
unique_countries <- sort(unique(CE_DF$CEvesFlagCou))

# Helper: add lon/lat centroids by looking up rectangle codes in the
# ICESrect reference table (already loaded in the main Rmd).
# Falls back to mapplots::ices.rect() if the column lookup fails.
# Always returns df with lon/lat columns; unrecognised codes get NA.
.add_lonlat <- function(df, rect_col) {
  if (nrow(df) == 0) {
    df$lon <- numeric(0)
    df$lat <- numeric(0)
    return(df)
  }
  df$lon <- NA_real_
  df$lat <- NA_real_

  # ICESRectAreas.csv has columns: ICESNAME, Area, MidLon, MidLat
  rect_id_col <- intersect(c("ICESNAME", "ICESname", "icesname",
                              "Rectangle", "StatRect", "Name"),
                           names(ICESrect))[1]
  lon_col     <- intersect(c("MidLon", "midlon", "Lon", "lon", "LON"),
                           names(ICESrect))[1]
  lat_col     <- intersect(c("MidLat", "midlat", "Lat", "lat", "LAT"),
                           names(ICESrect))[1]

  if (!is.na(rect_id_col) && !is.na(lon_col) && !is.na(lat_col)) {
    # Primary path: direct merge against ICESrect
    lookup <- ICESrect[, c(rect_id_col, lon_col, lat_col)]
    names(lookup) <- c("rect_key", "lon_new", "lat_new")
    merged <- merge(
      data.frame(rect_key = df[[rect_col]],
                 row_idx  = seq_len(nrow(df)),
                 stringsAsFactors = FALSE),
      lookup,
      by = "rect_key", all.x = TRUE, sort = FALSE
    )
    merged <- merged[order(merged$row_idx), ]
    df$lon <- merged$lon_new
    df$lat <- merged$lat_new

  } else {
    # Fallback: mapplots::ices.rect() — wrap each rectangle individually
    # to avoid length-mismatch when it doesn't vectorise properly
    message(".add_lonlat: ICESrect columns not found (",
            paste(names(ICESrect), collapse = ", "),
            "). Falling back to mapplots::ices.rect().")
    rects <- df[[rect_col]]
    lons  <- vapply(rects, function(r) {
      tryCatch(mapplots::ices.rect(r)$lon[1], error = function(e) NA_real_)
    }, numeric(1))
    lats  <- vapply(rects, function(r) {
      tryCatch(mapplots::ices.rect(r)$lat[1], error = function(e) NA_real_)
    }, numeric(1))
    df$lon <- lons
    df$lat <- lats
  }

  df
}

for (country in unique_countries) {

  CE_sub <- CE_DF %>%
    filter(CEvesFlagCou == country, CEstatRect != "-9") %>%
    distinct(CEstatRect, CEvesFlagCou, topMetiersW) %>%
    .add_lonlat("CEstatRect")

  CL_sub <- CL_DF %>%
    filter(CLvesFlagCou == country, CLstatRect != "-9") %>%
    distinct(CLstatRect, CLvesFlagCou, topMetiersW) %>%
    .add_lonlat("CLstatRect")

  # Skip country if no CE rectangles resolved to valid coordinates
  CE_valid <- filter(CE_sub, !is.na(lon) & !is.na(lat))
  if (nrow(CE_valid) == 0) next

  min.lon <- min(CE_valid$lon, na.rm = TRUE)
  max.lon <- max(CE_valid$lon, na.rm = TRUE)
  min.lat <- min(CE_valid$lat, na.rm = TRUE)
  max.lat <- max(CE_valid$lat, na.rm = TRUE)

  CL_without_CE[[country]] <- list()
  map_combined[[country]]  <- list()

  for (topMetier in sort(unique(CE_valid$topMetiersW))) {

    CE_tm <- filter(CE_sub, topMetiersW == topMetier, !is.na(lon), !is.na(lat))
    CL_tm <- filter(CL_sub, topMetiersW == topMetier, !is.na(lon), !is.na(lat))

    # Guard: if either subset is empty after coordinate filtering, skip
    if (nrow(CE_tm) == 0) next

    # Ensure both frames have lon/lat before anti_join (they always will after
    # .add_lonlat, but add zero-row fallback to be safe)
    if (nrow(CL_tm) == 0) {
      CL_only <- CL_tm %>% mutate(label = "CL Only")
    } else {
      CL_only <- anti_join(CL_tm, CE_tm, by = c("lon", "lat")) %>%
        mutate(label = "CL Only")
    }

    CL_without_CE[[country]][[topMetier]] <- CL_DF %>%
      filter(CLvesFlagCou == country,
             CLstatRect   != "-9",
             topMetiersW  == topMetier) %>%
      semi_join(CL_only, by = "CLstatRect") %>%
      select(CLid, CLvesFlagCou, CLyear, CLmonth, CLstatRect,
             CLmetier6, CLvesLenCat, CLencrypVesIds) %>%
      arrange(CLstatRect)

    make_map <- function(pts, title_str) {
      ggplot() +
        rdbes_theme() +
        geom_ices_squares(xlim = c(min.lon, max.lon), ylim = c(min.lat, max.lat),
                          linetype = "dotted", colour = "grey30", linewidth = 0.1) +
        geom_sf(data = world) +
        geom_point(data = pts, aes(lon, lat), size = 2, colour = "#e63946") +
        coord_sf(xlim = c(min.lon, max.lon), ylim = c(min.lat, max.lat)) +
        xlab("Longitude") + ylab("Latitude") +
        ggtitle(title_str)
    }

    map_combined[[country]][[topMetier]] <- ggarrange(
      make_map(CE_tm,   "CE"),
      make_map(CL_tm,   "CL"),
      make_map(CL_only, "CL without CE"),
      nrow = 1, ncol = 3
    )
  }
}
```

```{r spatial-maps-output, results="asis", echo=FALSE, warning=FALSE, fig.height=5, fig.width=15}
for (country in names(map_combined)) {
  catHeader(paste0(country, " {.tabset}"), 3)

  for (gear in names(map_combined[[country]])) {
    catHeader(gear, 4)
    cat("\n")
    print(map_combined[[country]][[gear]])
    cat("\n\n**Overview of CL records without CE**\n\n")
    cat("CL records for which no matching CE record exists (landings without effort).\n\n")
    print(htmltools::tagList(
      rdbes_dt(CL_without_CE[[country]][[gear]], caption = "CL records without CE", filter = "top")
    ))
    cat("\n")
  }
}
```
