
# CL and CE documentation

```{r doc-setup, include=FALSE}
# Ensure CLlanVal is numeric (may be character in some export formats)
CL$CLlanVal <- suppressWarnings(as.numeric(CL$CLlanVal))
```

```{r doc-helpers, include=FALSE}
# ---------------------------------------------------------------------------
# Helper: aggregate one CE metric by year / data basis / data source,
# then render a bar chart + datatable — avoids ~20x copy-paste blocks.
# ---------------------------------------------------------------------------
.ce_db_plot <- function(metric, y_label, title) {
  CEdb <- CE %>%
    group_by(CEyear, CEdBasSciEff, CEdSouSciEff) %>%
    summarise(value = sum(.data[[metric]], na.rm = TRUE), .groups = "drop")

  p <- ggplot(CEdb, aes(CEdBasSciEff, value, fill = CEdSouSciEff)) +
    geom_bar(stat = "identity") +
    facet_grid(. ~ CEyear, scales = "free") +
    theme_bw() +
    theme(text = element_text(size = 20),
          axis.text.x = element_text(angle = 90, hjust = 1)) +
    ylab(y_label) +
    ggtitle(title)
  print(p)

  names(CEdb)[names(CEdb) == "value"] <- metric
  print(datatable(CEdb, caption = title, rownames = FALSE,
                  options = list(dom = "t", scrollY = TRUE, pageLength = -1)))
}

# Helper: same pattern for CL
.cl_db_plot <- function(group_var, metric, y_label, title,
                        basis_col  = "CLdBasSciWeig",
                        source_col = "CLdSouSciWeig") {
  CLdb <- CL %>%
    group_by(across(all_of(c("CLyear", basis_col, source_col)))) %>%
    summarise(value = sum(.data[[metric]], na.rm = TRUE), .groups = "drop")

  p <- ggplot(CLdb, aes(.data[[basis_col]], value, fill = .data[[source_col]])) +
    geom_bar(stat = "identity") +
    facet_grid(. ~ CLyear, scales = "free") +
    theme_bw() +
    theme(text = element_text(size = 20),
          axis.text.x = element_text(angle = 90, hjust = 1)) +
    ylab(y_label) +
    ggtitle(title)
  print(p)

  names(CLdb)[names(CLdb) == "value"] <- metric
  print(datatable(CLdb, caption = title, rownames = FALSE,
                  options = list(dom = "t", scrollY = TRUE, pageLength = -1)))
}
```

## Data basis and data source {.tabset}

### OfficialWeight

```{r OfficialWeight}
.cl_db_plot(metric     = "CLoffWeight",
            y_label    = "Official weight (t)",
            title      = "Official weight by year, data basis and data source")
```

### ScientificWeight

```{r ScientificWeight}
.cl_db_plot(metric     = "CLsciWeight",
            y_label    = "Scientific weight (t)",
            title      = "Scientific weight by year, data basis and data source")
```

### LandingValue

```{r LandingValue}
.cl_db_plot(metric      = "CLlanVal",
            y_label     = "Landing value",
            title       = "Landing value by year, data basis and data source",
            source_col  = "CLdSouLanVal")
```

### NumberFractionalTrips

```{r NumberFractionalTrips}
.ce_db_plot("CEnumFracTrips",
            y_label = "Number of fractional trips",
            title   = "Number of fractional trips by year, data basis and data source")
```

### NumberDominantTrips

```{r NumberDominantTrips}
.ce_db_plot("CEnumDomTrip",
            y_label = "Number of dominant trips",
            title   = "Number of dominant trips by year, data basis and data source")
```

### OfficialDaysAtSea

```{r OfficialDaysAtSea}
.ce_db_plot("CEoffDaySea",
            y_label = "Official days at sea",
            title   = "Official days at sea by year, data basis and data source")
```

### ScientificDaysAtSea

```{r ScientificDaysAtSea}
.ce_db_plot("CEsciDaySea",
            y_label = "Scientific days at sea",
            title   = "Scientific days at sea by year, data basis and data source")
```

### OfficialFishingDays

```{r OfficialFishingDays}
.ce_db_plot("CEoffFishDay",
            y_label = "Official fishing days",
            title   = "Official fishing days by year, data basis and data source")
```

### ScientificFishingDays

```{r ScientificFishingDays}
.ce_db_plot("CEsciFishDay",
            y_label = "Scientific fishing days",
            title   = "Scientific fishing days by year, data basis and data source")
```

### OfficialVesselFishingHour

```{r OfficialVesselFishingHour}
.ce_db_plot("CEoffVesFishHour",
            y_label = "Official vessel fishing hours",
            title   = "Official vessel fishing hours by year, data basis and data source")
```

### ScientificVesselFishingHour

```{r ScientificVesselFishingHour}
.ce_db_plot("CEsciVesFishHour",
            y_label = "Scientific vessel fishing hours",
            title   = "Scientific vessel fishing hours by year, data basis and data source")
```

### OfficialkWDaysAtSea

```{r OfficialkWDaysAtSea}
.ce_db_plot("CEoffkWDaySea",
            y_label = "Official kW days at sea",
            title   = "Official kW days at sea by year, data basis and data source")
```

### ScientifickWDaysAtSea

```{r ScientifickWDaysAtSea}
.ce_db_plot("CEscikWDaySea",
            y_label = "Scientific kW days at sea",
            title   = "Scientific kW days at sea by year, data basis and data source")
```

### OfficialkWFishingDays

```{r OfficialkWFishingDays}
.ce_db_plot("CEoffkWFishDay",
            y_label = "Official kW fishing days",
            title   = "Official kW fishing days by year, data basis and data source")
```

### ScientifickWFishingDays

```{r ScientifickWFishingDays}
.ce_db_plot("CEscikWFishDay",
            y_label = "Scientific kW fishing days",
            title   = "Scientific kW fishing days by year, data basis and data source")
```

### OfficialkWFishingHours

```{r OfficialkWFishingHours}
.ce_db_plot("CEoffkWFishHour",
            y_label = "Official kW fishing hours",
            title   = "Official kW fishing hours by year, data basis and data source")
```

### ScientifickWFishingHours

```{r ScientifickWFishingHours}
.ce_db_plot("CEscikWFishHour",
            y_label = "Scientific kW fishing hours",
            title   = "Scientific kW fishing hours by year, data basis and data source")
```

### ScientificGTDaysAtSea

```{r ScientificGTDaysAtSea}
.ce_db_plot("CEgTDaySea",
            y_label = "Scientific GT days at sea",
            title   = "Scientific GT days at sea by year, data basis and data source")
```

### ScientificGTFishingDays

```{r ScientificGTFishingDays}
.ce_db_plot("CEgTFishDay",
            y_label = "Scientific GT fishing days",
            title   = "Scientific GT fishing days by year, data basis and data source")
```

### ScientificGTFishingHours

```{r ScientificGTFishingHours}
.ce_db_plot("CEgTFishHour",
            y_label = "Scientific GT fishing hours",
            title   = "Scientific GT fishing hours by year, data basis and data source")
```

### OfficialSoakingMeterHour

```{r OfficialSoakingMeterHour}
.ce_db_plot("CEoffSoakMeterHour",
            y_label = "Official soaking meter hours",
            title   = "Official soaking meter hours by year, data basis and data source")
```

### ScientificSoakingMeterHour

```{r ScientificSoakingMeterHour}
.ce_db_plot("CEsciSoakMeterHour",
            y_label = "Scientific soaking meter hours",
            title   = "Scientific soaking meter hours by year, data basis and data source")
```

### OfficialNumberHaulSets

```{r OfficialNumberHaulSets}
.ce_db_plot("CEoffNumHaulSet",
            y_label = "Official number of hauls/sets",
            title   = "Official number of hauls/sets by year, data basis and data source")
```

### ScientificNumberHaulSets

```{r ScientificNumberHaulSets}
.ce_db_plot("CEsciNumHaulSet",
            y_label = "Scientific number of hauls/sets",
            title   = "Scientific number of hauls/sets by year, data basis and data source")
```

### GearDimensions

```{r GearDimensions}
.ce_db_plot("CEgearDim",
            y_label = "Gear dimensions",
            title   = "Gear dimensions by year, data basis and data source")
```

## Metier allocation

Proportion of records assigned to the catch-all metier `MIS_MIS_0_0_0` relative to all records, by year.

```{r metier-mis-helper, include=FALSE}
# Helper: compute MIS vs non-MIS split and percentage for a given table + metric
.mis_table <- function(data, id_col, metric_col, caption_text) {
  mis_flag <- data[[id_col]] == "MIS_MIS_0_0_0"
  data$MIS_val <- ifelse(mis_flag,  data[[metric_col]], 0)
  data$ALL_val <- ifelse(!mis_flag, data[[metric_col]], 0)

  year_col <- if (grepl("^CL", id_col)) "CLyear" else "CEyear"

  result <- data %>%
    group_by(.data[[year_col]]) %>%
    summarise(
      MIS = sum(MIS_val, na.rm = TRUE),
      ALL = sum(ALL_val, na.rm = TRUE),
      .groups = "drop"
    ) %>%
    mutate(pct_MIS = format(round(MIS / (MIS + ALL) * 100, digits = 3), nsmall = 3))

  names(result)[names(result) == "MIS"] <- paste0(metric_col, "_MIS")
  names(result)[names(result) == "ALL"] <- paste0(metric_col, "_ALL")

  print(datatable(result, caption = caption_text, rownames = FALSE,
                  options = list(dom = "t", scrollY = TRUE, pageLength = -1)))
}
```

```{r OffWeightMIS}
.mis_table(CL, "CLmetier6", "CLoffWeight",
           "MIS_MIS_0_0_0 share by official weight")
```

```{r SciWeightMIS}
.mis_table(CL, "CLmetier6", "CLsciWeight",
           "MIS_MIS_0_0_0 share by scientific weight")
```

```{r LanValMIS}
.mis_table(CL, "CLmetier6", "CLlanVal",
           "MIS_MIS_0_0_0 share by landing value")
```

```{r OffFishingDaysMIS}
.mis_table(CE, "CEmetier6", "CEoffFishDay",
           "MIS_MIS_0_0_0 share by official fishing days")
```

```{r SciFishingDaysMIS}
.mis_table(CE, "CEmetier6", "CEsciFishDay",
           "MIS_MIS_0_0_0 share by scientific fishing days")
```

## Rectangle source {.tabset}

### OfficialWeightStatRect

```{r OffWeightStatRect}
CLdb <- CL %>%
  group_by(CLyear, CLdatBasStatRect, CLdSoucstatRect) %>%
  summarise(CLoffWeight = sum(CLoffWeight, na.rm = TRUE), .groups = "drop")

ggplot(CLdb, aes(CLdatBasStatRect, CLoffWeight, fill = CLdSoucstatRect)) +
  geom_bar(stat = "identity") +
  facet_grid(. ~ CLyear, scales = "free") +
  theme_bw() +
  theme(text = element_text(size = 20),
        axis.text.x = element_text(angle = 90, hjust = 1)) +
  ylab("Official weight (t)") +
  ggtitle("Official weight by year, data basis and source for statistical rectangle")

datatable(CLdb,
          caption  = "Official weight by year, data basis and source for statistical rectangle",
          rownames = FALSE,
          options  = list(dom = "t", scrollY = TRUE, pageLength = -1))
```

### OfficialFishingDaysStatRect

```{r FDStatRect}
# Bug fix: tab was labelled "OfficialWeightStatRect" (duplicate) in original —
# corrected to "OfficialFishingDaysStatRect" to match its actual content.
CEdb <- CE %>%
  group_by(CEyear, CEdatBasStatRect, CEsoucStatRect) %>%
  summarise(CEoffFishDay = sum(CEoffFishDay, na.rm = TRUE), .groups = "drop")

ggplot(CEdb, aes(CEdatBasStatRect, CEoffFishDay, fill = CEsoucStatRect)) +
  geom_bar(stat = "identity") +
  facet_grid(. ~ CEyear, scales = "free") +
  theme_bw() +
  theme(text = element_text(size = 20),
        axis.text.x = element_text(angle = 90, hjust = 1)) +
  ylab("Official fishing days") +
  ggtitle("Official fishing days by year, data basis and source for statistical rectangle")

datatable(CEdb,
          caption  = "Official fishing days by year, data basis and source for statistical rectangle",
          rownames = FALSE,
          options  = list(dom = "t", scrollY = TRUE, pageLength = -1))
```
