
```{r cs-guard, include=FALSE}
if (is.null(cs) || !is.data.frame(cs) || nrow(cs) == 0) {
  knitr::knit_exit()
}
```

# CS summary

```{r cs-packages, include=FALSE}
if (!requireNamespace("kableExtra", quietly = TRUE)) {
  install.packages("kableExtra", quiet = TRUE)
}
suppressPackageStartupMessages(library(kableExtra))
```

```{r cs-kable-helper, include=FALSE}
# ---------------------------------------------------------------------------
# Shared kable helper for the CS section — styled to match the report theme
# ---------------------------------------------------------------------------
cs_kable <- function(data, ...) {
  kable(data, align = "c", ...) |>
    kable_styling(
      bootstrap_options = c("striped", "hover"),
      full_width        = FALSE
    ) |>
    column_spec(1, width = "4cm") |>
    column_spec(seq(2, ncol(data)), width = "3cm")
}

# ---------------------------------------------------------------------------
# Helper: build a summary table (count of distinct IDs) by a grouping
# variable, add a Total row, and replace NAs with empty strings.
# Used by Tables 1, 2, 4, 5, 6, 7.
# ---------------------------------------------------------------------------
.cs_count_wide <- function(data, id_col, group_col,
                            row_col    = "Year/Hierarchy",
                            year_col   = "DEyear",
                            row_total  = TRUE) {
  data |>
    select(all_of(c(year_col, group_col, id_col))) |>
    filter(!is.na(.data[[id_col]]), .data[[id_col]] != "") |>
    distinct() |>
    group_by(across(all_of(c(year_col, group_col)))) |>
    count() |>
    arrange(.data[[group_col]]) |>
    pivot_wider(names_from  = all_of(group_col),
                values_from = n) |>
    rename(`Year/Hierarchy` = all_of(year_col)) |>
    rowwise() |>
    mutate(Total = sum(c_across(where(is.numeric)), na.rm = TRUE)) |>
    mutate(`Year/Hierarchy` = as.character(`Year/Hierarchy`)) -> out

  if (row_total) {
    total_row <- out |>
      ungroup() |>
      summarise(`Year/Hierarchy` = "Total",
                across(-`Year/Hierarchy`, sum, na.rm = TRUE))
    out <- bind_rows(out, total_row)
  }

  out |> mutate(across(everything(), ~ replace_na(as.character(.), "")))
}

# ---------------------------------------------------------------------------
# Helper: combine a "all" summary with a "subset" summary so that the
# subset counts appear in brackets next to the main count.
# ---------------------------------------------------------------------------
.cs_combine_bracket <- function(main_tbl, sub_tbl) {
  combined <- main_tbl |>
    left_join(sub_tbl, by = "Year/Hierarchy", suffix = c("", ".y"))

  combined <- combined |>
    mutate(across(ends_with(".y"),
                  ~ paste0("(", replace_na(as.character(.), "0"), ")")))

  for (col in setdiff(colnames(main_tbl), "Year/Hierarchy")) {
    combined[[col]] <- paste0(combined[[col]],
                              combined[[paste0(col, ".y")]])
  }

  combined |>
    select(-ends_with(".y")) |>
    mutate(
      across(everything(), ~ gsub("\\(NA\\)", "", .)),
      across(everything(), ~ gsub("\\(0\\)",  "", .)),
      across(everything(), ~ gsub("\\(\\)",   "", .))
    )
}
```

## Sample information

**Table 1.** Total number of Sampling Details (SD) records by hierarchy, including national and regional
routines. Counts for regional sampling schemes (`RegPilCF`, `RegPilIB`, `RegRouCF`) are shown in
brackets.

```{r cs-table1}
sd_all <- .cs_count_wide(cs, "SDid", "DEhierarchy")

sd_reg <- cs |>
  filter(DEsampSchemeType %in% c("RegPilCF", "RegPilIB", "RegRouCF")) |>
  .cs_count_wide("SDid", "DEhierarchy")

.cs_combine_bracket(sd_all, sd_reg) |>
  cs_kable(caption = "SD records by hierarchy and year")
```

**Table 2.** Total number of Sampling Details (SD) records by country, including national and regional
routines. Counts for regional sampling schemes are shown in brackets.

```{r cs-table2}
sd_all_ctry <- .cs_count_wide(cs, "SDid", "SDctry")

sd_reg_ctry <- cs |>
  filter(DEsampSchemeType %in% c("RegPilCF", "RegPilIB", "RegRouCF")) |>
  .cs_count_wide("SDid", "SDctry")

.cs_combine_bracket(sd_all_ctry, sd_reg_ctry) |>
  cs_kable(caption = "SD records by country and year")
```

## Samples data

### Number of species in Sample (SA)

**Table 3.** Number of unique species in Sample (SA) by hierarchy. The Total column and row give
unique species counts for the respective aggregation.

```{r cs-table3}
# Per-year, per-hierarchy unique species count
sa_spe <- cs |>
  select(DEhierarchy, DEyear, SAspeCode) |>
  filter(!is.na(SAspeCode)) |>
  distinct() |>
  group_by(DEyear, DEhierarchy) |>
  count() |>
  arrange(DEhierarchy) |>
  pivot_wider(names_from = DEhierarchy, values_from = n) |>
  rename(`Year/Hierarchy` = DEyear) |>
  mutate(`Year/Hierarchy` = as.character(`Year/Hierarchy`))

# Total unique species per year (across hierarchies)
sa_spe_total_col <- cs |>
  select(DEyear, SAspeCode) |>
  filter(!is.na(SAspeCode)) |>
  distinct() |>
  group_by(DEyear) |>
  count() |>
  rename(`Year/Hierarchy` = DEyear, Total = n) |>
  mutate(`Year/Hierarchy` = as.character(`Year/Hierarchy`))

sa_spe <- sa_spe |> left_join(sa_spe_total_col, by = "Year/Hierarchy")

# Total row: unique species per hierarchy (across all years)
sa_spe_row <- cs |>
  select(DEhierarchy, SAspeCode) |>
  distinct() |>
  group_by(DEhierarchy) |>
  count() |>
  arrange(DEhierarchy) |>
  pivot_wider(names_from = DEhierarchy, values_from = n) |>
  mutate(`Year/Hierarchy` = "Total")

sa_spe_row_total <- cs |>
  select(SAspeCode) |>
  distinct() |>
  count() |>
  rename(Total = n)

total_row <- cbind(sa_spe_row, sa_spe_row_total)

bind_rows(sa_spe, total_row) |>
  mutate(across(everything(), ~ replace_na(as.character(.), ""))) |>
  kable(align = "c",
        caption = "Unique species in SA by hierarchy and year") |>
  kable_styling(bootstrap_options = c("striped", "hover"),
                full_width = FALSE)
```

### Number of records in Frequency Measure (FM) and Biological Measurement (BV)

**Table 4.** Number of Frequency Measure (FM) records by hierarchy. Counts for lower hierarchy B are
shown in brackets.

```{r cs-table4}
fm_all <- .cs_count_wide(cs, "FMid", "DEhierarchy")

fm_b   <- cs |>
  filter(SAlowHierarchy == "B") |>
  .cs_count_wide("FMid", "DEhierarchy")

.cs_combine_bracket(fm_all, fm_b) |>
  cs_kable(caption = "FM records by hierarchy and year")
```

**Table 5.** Number of Frequency Measure (FM) records by country. Counts for lower hierarchy B are
shown in brackets.

```{r cs-table5}
fm_all_ctry <- .cs_count_wide(cs, "FMid", "SDctry")

fm_b_ctry   <- cs |>
  filter(SAlowHierarchy == "B") |>
  .cs_count_wide("FMid", "SDctry")

.cs_combine_bracket(fm_all_ctry, fm_b_ctry) |>
  cs_kable(caption = "FM records by country and year")
```

**Table 6.** Number of Biological Measurement (BV) records by hierarchy. Counts for lower hierarchy C
(under Sample SA) are shown in brackets.

```{r cs-table6}
bv_all  <- .cs_count_wide(cs, "BVid", "DEhierarchy")

bv_c    <- cs |>
  filter(SAlowHierarchy == "C") |>
  .cs_count_wide("BVid", "DEhierarchy")

.cs_combine_bracket(bv_all, bv_c) |>
  cs_kable(caption = "BV records by hierarchy and year")
```

**Table 7.** Number of Biological Measurement (BV) records by country. Counts for lower hierarchy C
are shown in brackets.

```{r cs-table7}
bv_all_ctry <- .cs_count_wide(cs, "BVid", "SDctry")

bv_c_ctry   <- cs |>
  filter(SAlowHierarchy == "C") |>
  .cs_count_wide("BVid", "SDctry")

.cs_combine_bracket(bv_all_ctry, bv_c_ctry) |>
  cs_kable(caption = "BV records by country and year")
```

### Types of biological measurements (BV)

**Table 8.** Biological measurement types per fish in Biological Measurement (BV), counted by country.
For hierarchies A and B, length information is taken from Frequency Measure (FM) when not present in BV.

```{r cs-table8}
# Pivot BV measurements wide so each type becomes its own column
cs_bv <- cs |>
  pivot_wider(names_from = BVtypeMeas, values_from = BVvalueMeas)

# Carry FM length measurements into BV when missing (hierarchies A/B)
cs_bv$ForkLength <- NA_character_

cs_bv <- cs_bv |>
  mutate(
    LengthTotal = ifelse(FMtypeMeas == "LengthTotal" &
                           (is.na(LengthTotal) | LengthTotal == ""),
                         FMclassMeas, LengthTotal),
    ForkLength  = ifelse(FMtypeMeas == "ForkLength" &
                           (is.na(ForkLength) | ForkLength == ""),
                         FMclassMeas, ForkLength)
  )

# Attach species and fish IDs — join via SAid (SA FK in BV) and BVfishId (BV PK)
species_ref <- cs |>
  select(SDctry, SAid, SAspeCode, SAspeCodeFAO, BVfishId) |>
  distinct()

cs_bv <- cs_bv |> left_join(species_ref)

# One row per individual fish (unique SAid + BVfishId combination)
cs_bv_fish <- cs_bv |>
  select(SDctry, SAid, SAspeCode, BVfishId,
         LengthTotal, Sex, WeightLive, Age, Maturity,
         OtolithCollected, WeightMeasured, InfoGenetic, InfoParasite,
         Stock, ScaleCollected, ForkLength) |>
  filter(!is.na(BVfishId), BVfishId != "") |>
  mutate(FishId = paste0(SAid, "_", BVfishId)) |>
  group_by(SDctry, SAspeCode, FishId) |>
  summarise(
    LengthTotal      = first(na.omit(LengthTotal)),
    ForkLength       = first(na.omit(ForkLength)),
    Sex              = first(na.omit(Sex)),
    WeightLive       = first(na.omit(WeightLive)),
    Age              = first(na.omit(Age)),
    Maturity         = first(na.omit(Maturity)),
    OtolithCollected = first(na.omit(OtolithCollected)),
    WeightMeasured   = first(na.omit(WeightMeasured)),
    InfoGenetic      = first(na.omit(InfoGenetic)),
    InfoParasite     = first(na.omit(InfoParasite)),
    Stock            = first(na.omit(Stock)),
    ScaleCollected   = first(na.omit(ScaleCollected)),
    .groups = "drop"
  )

cs_bv_fish |>
  select(FishId, SDctry, LengthTotal, ForkLength, Sex, WeightLive, Age,
         Maturity, OtolithCollected, WeightMeasured, InfoGenetic,
         InfoParasite, Stock, ScaleCollected) |>
  group_by(SDctry) |>
  summarise(
    LengthTotal      = sum(!is.na(LengthTotal)),
    ForkLength       = sum(!is.na(ForkLength)),
    Sex              = sum(!is.na(Sex)),
    WeightLive       = sum(!is.na(WeightLive)),
    Age              = sum(!is.na(Age)),
    Maturity         = sum(!is.na(Maturity)),
    OtolithCollected = sum(!is.na(OtolithCollected)),
    WeightMeasured   = sum(!is.na(WeightMeasured)),
    InfoGenetic      = sum(!is.na(InfoGenetic)),
    InfoParasite     = sum(!is.na(InfoParasite)),
    Stock            = sum(!is.na(Stock)),
    ScaleCollected   = sum(!is.na(ScaleCollected)),
    .groups = "drop"
  ) |>
  kable(format.args = list(big.mark = " "),
        caption = "BV measurement types per fish by country (including NAs)") |>
  kable_styling(bootstrap_options = c("striped", "hover"), full_width = FALSE)
```

**Table 9.** Same as Table 8 but excluding records where `BVvalueMeas` is `NA` or empty.

```{r cs-table9}
cs_bv_fish |>
  select(FishId, SDctry, LengthTotal, ForkLength, Sex, WeightLive, Age,
         Maturity, OtolithCollected, WeightMeasured, InfoGenetic,
         InfoParasite, Stock, ScaleCollected) |>
  group_by(SDctry) |>
  summarise(
    LengthTotal      = sum(!is.na(LengthTotal) & LengthTotal      != ""),
    ForkLength       = sum(!is.na(ForkLength)  & ForkLength       != ""),
    Sex              = sum(!is.na(Sex)          & Sex              != ""),
    WeightLive       = sum(!is.na(WeightLive)   & WeightLive       != ""),
    Age              = sum(!is.na(Age)           & Age              != ""),
    Maturity         = sum(!is.na(Maturity)      & Maturity         != ""),
    OtolithCollected = sum(!is.na(OtolithCollected) & OtolithCollected != ""),
    WeightMeasured   = sum(!is.na(WeightMeasured)   & WeightMeasured   != ""),
    InfoGenetic      = sum(!is.na(InfoGenetic)   & InfoGenetic      != ""),
    InfoParasite     = sum(!is.na(InfoParasite)  & InfoParasite     != ""),
    Stock            = sum(!is.na(Stock)          & Stock            != ""),
    ScaleCollected   = sum(!is.na(ScaleCollected) & ScaleCollected   != ""),
    .groups = "drop"
  ) |>
  kable(format.args = list(big.mark = " "),
        caption = "BV measurement types per fish by country (non-empty values only)") |>
  kable_styling(bootstrap_options = c("striped", "hover"), full_width = FALSE)
```

### BV categorical value distributions

Frequency counts for key categorical biological variables, broken down by country.

```{r cs-bv-distributions}
# Sex
cs_bv_fish |>
  filter(!is.na(Sex)) |>
  group_by(SDctry, Sex) |>
  count() |>
  kable(format.args = list(big.mark = " "),
        caption = "Sex distribution by country") |>
  kable_styling(bootstrap_options = c("striped", "hover"), full_width = FALSE)

# Maturity
cs_bv_fish |>
  filter(!is.na(Maturity)) |>
  group_by(SDctry, Maturity) |>
  count() |>
  kable(format.args = list(big.mark = " "),
        caption = "Maturity distribution by country") |>
  kable_styling(bootstrap_options = c("striped", "hover"), full_width = FALSE)

# Otolith collected
cs_bv_fish |>
  filter(!is.na(OtolithCollected)) |>
  group_by(SDctry, OtolithCollected) |>
  count() |>
  kable(format.args = list(big.mark = " "),
        caption = "OtolithCollected distribution by country") |>
  kable_styling(bootstrap_options = c("striped", "hover"), full_width = FALSE)

# Age
cs_bv_fish |>
  filter(!is.na(Age)) |>
  group_by(SDctry, Age) |>
  count() |>
  kable(format.args = list(big.mark = " "),
        caption = "Age distribution by country") |>
  kable_styling(bootstrap_options = c("striped", "hover"), full_width = FALSE)

# Parasite information
cs_bv_fish |>
  filter(!is.na(InfoParasite)) |>
  group_by(SDctry, InfoParasite) |>
  count() |>
  kable(format.args = list(big.mark = " "),
        caption = "InfoParasite distribution by country") |>
  kable_styling(bootstrap_options = c("striped", "hover"), full_width = FALSE)

# Genetic information
cs_bv_fish |>
  filter(!is.na(InfoGenetic)) |>
  group_by(SDctry, InfoGenetic) |>
  count() |>
  kable(format.args = list(big.mark = " "),
        caption = "InfoGenetic distribution by country") |>
  kable_styling(bootstrap_options = c("striped", "hover"), full_width = FALSE)
```
