---
title: "RDBES National Quality Report"
output: 
  html_document:
    self_contained: true
    toc: true
    toc_depth: 4
    number_sections: true
    toc_float:
      collapsed: true
      smooth_scroll: true
    theme: flatly
    highlight: kate
params:
  RDBESfile:        !r c("", "")
  eurostat:         FALSE
  prelcatchstat:    FALSE
  prelcatchFile:    ""
  fleetRegister:    FALSE
  fleetRegisterFile: ""
  BA_NANSEA: BA_NANSEA
---

```{r setup, include=FALSE}
# Use a per-session temp directory for figures so no figure-html folder is
# created on disk. The report is self_contained so all figures are
# base64-embedded in the HTML anyway; the on-disk copies are never needed.
knitr::opts_chunk$set(
  echo       = FALSE,
  warning    = FALSE,
  message    = FALSE,
  error      = FALSE,
  fig.height = 10,
  fig.width  = 14,
  fig.path   = file.path(tempdir(), "rdbes-figures", "/")
)
options(scipen = 999)
options(viewer = function(...) invisible(NULL))
```

```{css report-style, echo=FALSE}
/* ── Typography ─────────────────────────────────────────────── */
body        { font-family: "Helvetica Neue", Helvetica, Arial, sans-serif;
              font-size: 14px; color: #2c2c2c; line-height: 1.6; }
h1, h2, h3  { font-weight: 600; color: #1a3a4a; }
h1          { border-bottom: 2px solid #2a9d8f; padding-bottom: 6px; }
h2          { border-bottom: 1px solid #dee2e6; padding-bottom: 4px; }
p           { color: #3d3d3d; }

/* ── TOC ─────────────────────────────────────────────────────── */
#TOC        { background: #f8fafc; border: 1px solid #e2e8f0;
              border-radius: 6px; padding: 12px 16px; font-size: 13px; }
#TOC a      { color: #2a9d8f; }
#TOC a:hover{ color: #1a6b61; text-decoration: underline; }

/* ── Tables (DT) ─────────────────────────────────────────────── */
.dataTables_wrapper { font-size: 13px; margin-bottom: 1.5em; }
table.dataTable thead th {
  background: #1a3a4a; color: #ffffff; font-weight: 600;
  border-bottom: 2px solid #2a9d8f !important; }
table.dataTable tbody tr:hover { background: #eef7f6 !important; }
.dt-button   { background: #2a9d8f !important; color: #fff !important;
               border: none !important; border-radius: 4px !important;
               padding: 4px 10px !important; font-size: 12px !important; }
.dt-button:hover { background: #21867a !important; }

/* ── Callout box for intro text ──────────────────────────────── */
.callout     { background: #eef7f6; border-left: 4px solid #2a9d8f;
               padding: 10px 16px; border-radius: 0 6px 6px 0;
               margin-bottom: 1em; font-size: 13px; color: #2c4a48; }
```

```{r packages, include=FALSE}
# Install missing packages automatically
required_packages <- c(
  "icesVocab", "tidyverse", "eurostat", "DT",
  "rnaturalearth", "rnaturalearthdata", "sf", "mapplots",
  "ggpubr", "remotes", "htmltools",
  "knitr", "rstudioapi", "ggalluvial", "RColorBrewer", "viridis"
)
new_packages <- required_packages[!(required_packages %in% installed.packages()[, "Package"])]
if (length(new_packages)) install.packages(new_packages, quiet = TRUE)

suppressPackageStartupMessages({
  library(icesVocab)
  library(tidyverse)
  library(eurostat)
  library(DT)
  library(rnaturalearth)
  library(rnaturalearthdata)
  library(sf)
  library(knitr)
  library(mapplots)
  library(ggpubr)
  library(htmltools)
  library(ggalluvial)
  library(RColorBrewer)
})
```

```{r load-utils, include=FALSE}
# Source utility functions (path relative to this .Rmd file)
source(file.path(dirname(knitr::current_input(dir = TRUE)), "..", "utils", "utils.R"))
```

```{r shared-style, include=FALSE}
# ---------------------------------------------------------------------------
# Shared ggplot theme and colour palette used by every plot in this report
# ---------------------------------------------------------------------------
rdbes_theme <- function(...) {
  theme_minimal(base_size = 12, base_family = "sans") +
    theme(
      axis.text.x      = element_text(angle = 45, hjust = 1, colour = "grey30"),
      axis.text.y      = element_text(colour = "grey30"),
      axis.title       = element_text(size = 11, colour = "grey20"),
      axis.line        = element_line(colour = "grey80"),
      legend.title     = element_text(size = 10, face = "bold"),
      legend.text      = element_text(size = 9),
      legend.key.size  = unit(0.7, "cm"),
      legend.position  = "right",
      strip.text       = element_text(size = 10, face = "bold", colour = "grey20"),
      strip.background = element_rect(fill = "#eef2f7", colour = NA),
      panel.grid.major = element_line(colour = "grey92", linewidth = 0.4),
      panel.grid.minor = element_blank(),
      panel.border     = element_blank(),
      plot.title       = element_text(size = 12, face = "bold", colour = "grey15", hjust = 0),
      plot.subtitle    = element_text(size = 10, colour = "grey40", hjust = 0),
      plot.margin      = margin(8, 8, 8, 8),
      ...
    )
}

# Discrete colour palettes — consistent across all plots
RDBES_PALETTE <- c("#2a9d8f", "#e76f51", "#457b9d", "#e9c46a",
                   "#264653", "#f4a261", "#a8dadc", "#e63946",
                   "#3498db")

RDBES_FILL <- scale_fill_manual(values = RDBES_PALETTE)
RDBES_COL  <- scale_colour_manual(values = RDBES_PALETTE)

# ---------------------------------------------------------------------------
# Shared DT helper — all tables get the same look + Excel export button
# ---------------------------------------------------------------------------
rdbes_dt <- function(data, caption = NULL, filter = "none", ...) {
  DT::datatable(
    data,
    caption    = caption,
    filter     = filter,
    rownames   = FALSE,
    extensions = "Buttons",
    class      = "stripe hover compact",
    options    = list(
      dom        = "Blfrtip",
      buttons    = list(
        list(extend = "excel",
             text   = "<i class='fas fa-file-excel'></i> Excel",
             title  = if (!is.null(caption)) caption else "RDBES export")
      ),
      lengthMenu = list(c(10, 25, 50, -1), c("10", "25", "50", "All")),
      pageLength = 10,
      scrollX    = TRUE
    ),
    ...
  )
}
```

```{r load-aux-data, include=FALSE}
# RCG area lookup
rcg_url   <- "https://raw.githubusercontent.com/ices-eg/RCGs/master/Metiers/Reference_lists/AreaRegionLookup.csv"
Area <- read.csv(rcg_url, header = TRUE, stringsAsFactors = FALSE)

# Fix known trailing-whitespace issue in RCG region codes (issue observed upstream)
Area <- Area %>%
  mutate(Code = trimws(Code)) %>%
  select(AreaCode, Code)

# ICES rectangle reference list
rect_url  <- "https://github.com/ices-tools-dev/RDBES/raw/master/QC-scripts/RectangleList/ICESRectAreas.csv"
ICESrect  <- read.csv(rect_url, header = TRUE, stringsAsFactors = FALSE)
```

```{r load-rdbes, include=FALSE}
# Read RDBES CL and CE tables
# read.rdbes() returns a named list: list(CL = ..., CE = ...)
df <- read.rdbes(params$RDBESfile)
CL <- df$CL
CE <- df$CE

# Derive metier levels 4 and 5 from metier level 6
CL <- CL %>% mutate(
  CLmetier4 = str_extract(CLmetier6, "[^_]+"),
  CLmetier5 = str_extract(CLmetier6, "[^_]*_[^_]*")
)
CE <- CE %>% mutate(
  CEmetier4 = str_extract(CEmetier6, "[^_]+"),
  CEmetier5 = str_extract(CEmetier6, "[^_]*_[^_]*")
)
```

```{r report-title, include=FALSE}
clY <- sort(unique(CL$CLyear))
ceY <- sort(unique(CE$CEyear))

if (length(clY) > 1 && identical(clY, ceY)) {
  titleR <- paste("National quality report for years", paste(clY, collapse = ", "))
} else {
  titleR <- paste("National quality report for year", paste(clY, collapse = ", "))
}

# Update the HTML <title> tag dynamically from the data
rmarkdown::output_metadata$set(title = titleR)
```


```{r species-lookup, include=FALSE}
# Fetch species scientific names via AphiaID
ScName <- getCodeList("SpecWorms") %>%
  select(Description, Key) %>%
  rename(LatinName = Description)

# CLspecCode is integer from the CSV; Key from icesVocab is character — align before joining
CL$CLspecCode <- as.character(CL$CLspecCode)

CL <- left_join(CL, ScName, by = c("CLspecCode" = "Key"))
```

```{r weight-kg-to-t, include=FALSE}
# Convert weights from kg to tonnes
CL <- CL %>%
  mutate(
    CLoffWeight = round(CLoffWeight / 1000, digits = 0),
    CLsciWeight = round(CLsciWeight / 1000, digits = 0)
  )
```

<div class="callout">
This report has been developed under the WGRBDES-GOV ISSG Data Quality. Its primary purpose is to serve as a resource for data submitters, helping them identify and correct potential errors before the submission deadline. By utilising this script, data submitters can improve the accuracy and completeness of their data, thereby improving the overall quality and reliability of the submitted information.
</div>

# Summary

The following tables show summary values between the years. <span style="color:red">Differences exceeding 30% relative to the most recent year are highlighted in red.</span>

```{r summary-records}
# Number of records per year
CLr <- CL %>%
  group_by(CLyear) %>%
  count() %>%
  mutate(Dataset = "CL") %>%
  rename(Year = CLyear)

CEr <- CE %>%
  group_by(CEyear) %>%
  count() %>%
  mutate(Dataset = "CE") %>%
  rename(Year = CEyear)

tabN1 <- bind_rows(CLr, CEr) %>%
  group_by(Dataset) %>%
  mutate(
    ref   = n[which.max(Year)],
    inRange = n <= ref * 1.3 & n >= ref * 0.7
  ) %>%
  select(Year, n, inRange, Dataset)

tabN_wide  <- tabN1 %>% select(-inRange) %>% pivot_wider(names_from = Year, values_from = n)
tabN_flags <- tabN1 %>% select(-n)       %>% pivot_wider(names_from = Year, values_from = inRange)
year_cols  <- setdiff(names(tabN_wide), "Dataset")

.flag_dt <- function(wide, flags, caption) {
  dt <- rdbes_dt(wide, caption = caption)
  for (yr in intersect(year_cols, names(wide))) {
    ok  <- flags[[yr]]
    vals <- wide[[yr]]
    dt <- DT::formatStyle(dt, yr,
      backgroundColor = DT::styleEqual(vals, ifelse(ok, "transparent", "#ffe8e8")),
      color           = DT::styleEqual(vals, ifelse(ok, "inherit",     "#c0392b")),
      fontWeight      = DT::styleEqual(vals, ifelse(ok, "normal",      "bold")))
  }
  dt
}

.flag_dt(tabN_wide, tabN_flags, "Number of records in the CE and CL tables by year")
```

```{r summary-metiers}
# Number of unique metier level 6 per year
CLm <- CL %>%
  group_by(CLyear) %>%
  summarise(Nmet = n_distinct(CLmetier6), .groups = "drop") %>%
  mutate(Dataset = "CL") %>%
  rename(Year = CLyear)

CEm <- CE %>%
  group_by(CEyear) %>%
  summarise(Nmet = n_distinct(CEmetier6), .groups = "drop") %>%
  mutate(Dataset = "CE") %>%
  rename(Year = CEyear)

tabm1 <- bind_rows(CLm, CEm) %>%
  group_by(Dataset) %>%
  mutate(
    ref     = Nmet[which.max(Year)],
    inRange = Nmet <= ref * 1.3 & Nmet >= ref * 0.7
  ) %>%
  select(Year, Nmet, inRange, Dataset)

tabm_wide  <- tabm1 %>% select(-inRange) %>% pivot_wider(names_from = Year, values_from = Nmet)
tabm_flags <- tabm1 %>% select(-Nmet)    %>% pivot_wider(names_from = Year, values_from = inRange)

.flag_dt(tabm_wide, tabm_flags, "Number of unique metiers level 6 in the CE and CL tables by year")
```

```{r summary-vessels}
# Number of unique encrypted vessel IDs per year
CLv <- CL %>%
  select(CLyear, CLencrypVesIds) %>%
  distinct() %>%
  separate_rows(CLencrypVesIds, convert = FALSE) %>%
  distinct() %>%
  group_by(CLyear) %>%
  summarise(NumberOfUniqueVessels = n_distinct(CLencrypVesIds), .groups = "drop") %>%
  mutate(Dataset = "CL") %>%
  rename(Year = CLyear)

CEv <- CE %>%
  select(CEyear, CEencrypVesIds) %>%
  distinct() %>%
  separate_rows(CEencrypVesIds, convert = FALSE) %>%
  distinct() %>%
  group_by(CEyear) %>%
  summarise(NumberOfUniqueVessels = n_distinct(CEencrypVesIds), .groups = "drop") %>%
  mutate(Dataset = "CE") %>%
  rename(Year = CEyear)

tabv1 <- bind_rows(CLv, CEv) %>%
  group_by(Dataset) %>%
  mutate(
    ref     = NumberOfUniqueVessels[which.max(Year)],
    inRange = NumberOfUniqueVessels <= ref * 1.3 & NumberOfUniqueVessels >= ref * 0.7
  ) %>%
  select(Year, NumberOfUniqueVessels, inRange, Dataset) %>%
  rename(Nves = NumberOfUniqueVessels)

tabv_wide  <- tabv1 %>% select(-inRange) %>% pivot_wider(names_from = Year, values_from = Nves)
tabv_flags <- tabv1 %>% select(-Nves)    %>% pivot_wider(names_from = Year, values_from = inRange)

.flag_dt(tabv_wide, tabv_flags, "Number of unique vessels in the CE and CL tables by year")
```

```{r eval-auxiliary, include=FALSE}
doNextChunk <- any(c(params$eurostat, params$prelcatchstat, params$fleetRegister))
```

```{r aux-header, results='asis', eval=doNextChunk}
cat("# Comparison with auxiliary data sources")
```

```{r load-eurostat, eval=params$eurostat}
# Eurostat landed weight by country (tag00076)
eurostatW <- get_eurostat(
  "tag00076",
  time_format    = "num",
  filters        = list(geo = unique(CL$CLlanCou)),
  stringsAsFactors = FALSE
)
```

```{r child-eurostat, child='01_Eurostat.Rmd', eval=params$eurostat}
```

```{r load-prelcatch, eval=params$prelcatchstat}
prelC <- read.prelC(params$prelcatchFile)
```

```{r child-prelcatch, child='02_PreliminaryCatches.Rmd', eval=params$prelcatchstat}
```

```{r load-fleet, eval=params$fleetRegister}
fleet <- read.fleet(params$fleetRegisterFile)
```

```{r child-fleet, child='03_FleetRegister.Rmd', eval=params$fleetRegister}
```

```{r child-cl, child='04_CL_Multiannual.Rmd'}
```

```{r child-ce, child='05_CE_Multiannual.Rmd'}
```

```{r child-clce, child='06_CLCE_compare.Rmd'}
```

```{r child-spatial, child='07_Spatial_checks.Rmd', eval=params$BA_NANSEA}
```

```{r child-documentation, child='08_CE_CL_documentation.Rmd'}
```
