---
# date: "`r format(Sys.time(), '%d %B, %Y')`"
output: 
  html_document:
    toc: true
    toc_depth: 4
    number_sections: true
    toc_float: true
params:
  RDBESfile: RDBESfile
  eurostat: eurostat
  prelcatchstat: prelcatchstat
  prelcatchFile: prelcatchFile
  fleetRegister: fleetRegister
  fleetRegisterFile: fleetRegisterFile
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE, fig.height = 10, fig.width = 14)
options(scipen=999, viewer=NULL)
```

```{r}
# Packages 
# Installs missing packages automatically 
list.of.packages <- c("icesVocab", "tidyverse", "eurostat", "DT", "rnaturalearth", "rnaturalearthdata", "sf", "mapplots", "kableExtra", "ggpubr", "remotes", "htmltools", "knitr", "rstudioapi")
new.packages <- list.of.packages[!(list.of.packages %in% installed.packages()[,"Package"])]
if(length(new.packages)) install.packages(new.packages)

# if(!"RDBEScore" %in% installed.packages()[,"Package"]){
#   remotes::install_github("ices-tools-dev/RDBEScore", build_vignettes = TRUE)
# }

# Loads packages 
library(icesVocab)
library(tidyverse, quietly = TRUE)
library(eurostat)
library(DT)
library(rnaturalearth)
library(rnaturalearthdata)
library(sf)
library(knitr)
library(mapplots)
library(kableExtra)
library(ggpubr)
# library(RDBEScore)
library(htmltools)

```


```{r}
# Functions 
source(paste0(dirname(rstudioapi::getActiveDocumentContext()$path), "/utils/utils.R"))
```

```{r}
# Read auxiliary files 
# RCG areas 
url <- "https://raw.githubusercontent.com/ices-eg/RCGs/master/Metiers/Reference_lists/AreaRegionLookup.csv"
Area <- read.csv(url, header = TRUE)
### Fix the extra space in rcg region code
Area <- mutate(Area, Code = ifelse(Code %in% "NSEA                                    " , "NSEA",
                             ifelse(Code %in% "NAtl                                      ", "NAtl", Code))) %>%
  select(AreaCode, Code)

#Read the rectangle list from the repository 
url <- "https://github.com/ices-tools-dev/RDBES/raw/master/QC-scripts/RectangleList/ICESRectAreas.csv"
ICESrect <- read.csv(url, header = TRUE)

```



```{r}
# Read RDBES CL, CE files 
# Needs to be updated
# df <- createRDBESDataObject(input = params$RDBESfile) 
# For now use this 
df <- read.rdbes(params$RDBESfile)
CL <- as.data.frame(df[1])
CE <- as.data.frame(df[2])

# # Change class of some fields for plotting 
# CL <- rdbes.fc(CL)
# # Quick fix of CE col names - inconsistency between CE-CL lowercase and upper case for some fields 
# names(CE)[names(CE) == 'CEMonth'] <- 'CEmonth'
# names(CE)[names(CE) == 'CEArea'] <- 'CEarea'
# CE <- rdbes.fc(CE)


## Get metier lvl 4 
CL <- mutate(CL, CLmetier4 = str_extract(CLmetier6, "[^_]+"))
CE <- mutate(CE, CEmetier4 = str_extract(CEmetier6, "[^_]+"))

## Get metier lvl 5 
CL <- mutate(CL, CLmetier5 = str_extract(CLmetier6,  "[^_]*_[^_]*"))
CE <- mutate(CE, CEmetier5 = str_extract(CEmetier6,  "[^_]*_[^_]*"))
```

```{r}
clY <- sort(unique(CL$CLyear))
ceY <- sort(unique(CE$CEyear))
# TODO add consistency checks between CL and CE and add warning for the comparison of both if there are
# no matching years 

if(all(clY == ceY) & length(unique(clY)) > 1){
  titleR <- paste("National quality report for years", paste(clY, collapse = ", "))
}else{
  titleR <- paste("National quality report for year ", clY)
}
```

---
title: `r titleR`
---



```{r}
# Processing 
# Get species scientific name from aphiaID
ScName <- getCodeList("SpecWorms") %>%
  select(Description, Key) %>%
  rename(LatinName = Description)
CL <- left_join(CL, ScName, by = c("CLspecCode" = "Key")) 
```

```{r}
# Transform kg to t 
CL$CLoffWeight <- round(CL$CLoffWeight/1000, digits = 0)
CL$CLsciWeight <- round(CL$CLsciWeight/1000, digits = 0)
```



This report has been developed under the WGRBDES-GOV ISSG Data Quality. Its primary purpose is to serve as a resource for data submitters, helping them identify and correct potential errors before the submission deadline. By utilizing this script, data submitters can improve the accuracy and completeness of their data, thereby improving the overall quality and reliability of the submitted information. The output shown herein is designed to assist users in reviewing their data, facilitating a smoother and more efficient submission process. 

# Summary 

The following tables show summary values between the years. <span style="color:red">If the difference between the years when compared to the most recent year exceeds 30% they are highlighted red. </span> 

```{r}
# Number of records 
CLr <- CL %>%
  group_by(CLyear) %>%
  count() %>%
  mutate(Dataset = "CL") %>%
  rename(Year = CLyear)
CEr <- CE %>%
  group_by(CEyear) %>%
  count() %>%
  mutate(Dataset = "CE") %>%
  rename(Year = CEyear)

tabN1 <- rbind(CLr, CEr)  %>%
  group_by(Dataset) %>%
  mutate(Pos =  (0.3 * n[which.max(Year)] + n[which.max(Year)]),
         Neg = abs(0.3 * n[which.max(Year)] - n[which.max(Year)]),
         n = cell_spec(n, color = ifelse(n <= Pos & n >= Neg, "black", "red")))

tabN2 <- tabN1 %>%
  select(Year, n, Dataset) %>%
  spread(Year, n) 


kbl(tabN2, escape = F, caption = "Number of records in the CE and CL tables by year", align = rep("c", ncol(tabN2))) %>%
  kable_styling(bootstrap_options = "striped" )

```


```{r}
# Numbers of metier lvl 6 
CLm <- CL %>%
  group_by(CLyear) %>%
  summarise(Nmet = length(unique(CLmetier6))) %>%
  mutate(Dataset = "CL") %>%
  rename(Year = CLyear)
CEm <- CE %>%
  group_by(CEyear) %>%
  summarise(Nmet = length(unique(CEmetier6))) %>%
  mutate(Dataset = "CE") %>%
  rename(Year = CEyear)

tabm1 <- rbind(CLm, CEm) %>%
  group_by(Dataset) %>%
  mutate(Pos =  (0.3 * Nmet[which.max(Year)] + Nmet[which.max(Year)]),
         Neg = abs(0.3 * Nmet[which.max(Year)] - Nmet[which.max(Year)]),
         Nmet = cell_spec(Nmet, color = ifelse(Nmet <= Pos & Nmet >= Neg, "black", "red")))

tabm2 <- tabm1 %>%
  select(Year, Nmet, Dataset) %>%
  spread(Year, Nmet) 


kbl(tabm2, escape = F, caption = "Number of unique metiers level 6 in the CE and CL tables by year", align = rep("c", ncol(tabm2))) %>%
  kable_styling(bootstrap_options = "striped")


```

```{r}
# Number of unique vessels by year 

CLv <- select(CL, CLyear, CLencrypVesIds) %>%
  distinct() %>%
  separate_rows(CLencrypVesIds, convert = TRUE) %>%
  distinct() %>%
  group_by(CLyear) %>%
  summarise(NumberOfUniqueVessels = length(unique(CLencrypVesIds))) %>%
  mutate(Dataset = "CL") %>%
  rename(Year = CLyear)
CEv <- select(CE, CEyear, CEencrypVesIds) %>%
  distinct() %>%
  separate_rows(CEencrypVesIds, convert = TRUE) %>%
  distinct()%>%
  group_by(CEyear) %>%
  summarise(NumberOfUniqueVessels = length(unique(CEencrypVesIds)))%>%
  mutate(Dataset = "CE") %>%
  rename(Year = CEyear)

tabv1 <- rbind(CLv, CEv) %>%
  group_by(Dataset) %>%
  mutate(Pos =  (0.3 * NumberOfUniqueVessels[which.max(Year)] + NumberOfUniqueVessels[which.max(Year)]),
         Neg = abs(0.3 * NumberOfUniqueVessels[which.max(Year)] - NumberOfUniqueVessels[which.max(Year)]),
         Nmet = cell_spec(NumberOfUniqueVessels, color = ifelse(NumberOfUniqueVessels <= Pos & NumberOfUniqueVessels >= Neg, "black", "red")))

tabv2 <- tabv1 %>%
  select(Year, NumberOfUniqueVessels, Dataset) %>%
  spread(Year, NumberOfUniqueVessels) 


kbl(tabv2, escape = F, caption = "Number of unique vessels in the CE and CL tables by year", align = rep("c", ncol(tabv2))) %>%
  kable_styling(bootstrap_options = "striped")

```


```{r}
# Number of species
CLsp <- CL %>%
  group_by(CLyear) %>%
  summarise(NumberOfSpecies = length(unique(CLspecCode)))

```


```{r}
# Run next chunk? 
doNextChunk <- any(c(params$eurostat, params$prelcatchstat, params$fleetRegister))
```


```{r, results='asis', eval = doNextChunk}
cat("# Comparison with auxiliary data sources")
```



```{r, eval = params$eurostat}
# Auxiliary information for comparisons 
# 1. Eurostat data - weight 
eurostatW <- get_eurostat("tag00076", time_format = "num", filters = list(geo = unique(CL$CLlanCou)), stringsAsFactors = TRUE) # tag corresponds to catches in all fishing regions by country
# https://ec.europa.eu/eurostat/databrowser/view/tag00076/default/table?lang=en&category=t_fish

# 2. Eurostat data - number of vessels 
# eurostatV <- get_eurostat("tag00076", time_format = "num", filters = list(geo = unique(CL$CLlandingCountry)), stringsAsFactors = TRUE)

```

```{r,  child = '01_Eurostat.Rmd', eval = params$eurostat}

```

```{r, eval = params$prelcatchstat}
# 2. ICES preliminary catches
prelC <- read.prelC(params$prelcatchFile)
```


```{r,  child = '02_PreliminaryCatches.Rmd', eval = params$prelcatchstat}

```


```{r, eval = params$fleetRegister}
# 3. Fleet register 
fleet <- read.fleet(params$fleetRegisterFile)
```

```{r, child = '03_FleetRegister.Rmd', eval = params$fleetRegister}

```


```{r, child = '04_CL_Multiannual.Rmd'}

```


```{r, child = '05_CE_Multiannual.Rmd'}

```


```{r, child = '06_CLCE_compare.Rmd'}

```


```{r, child = '07_Spatial_checks.Rmd'}

```



