```{r title, include = F}

front_title <- "RDBES CL Multinational overviews"

```

---
title: `r front_title`
author: "ICES RDBES ISSG Quality"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = FALSE, message = FALSE)
options(scipen=999)
```

```{r, echo=FALSE, message=FALSE, warning = FALSE}
# Packages 
# TODO add automatic install for packages if they do not exist 
library(icesVocab)
library(tidyverse)
library(eurostat)
library(RDBEScore)
library(rnaturalearth)
library(rnaturalearthdata)
library(sf)
library(mapplots)
library(kableExtra)
library(ggpubr)
```

```{r ReadData, echo=FALSE, message=FALSE, warning = FALSE}
CE <- createRDBESDataObject("../../../1. NDGP/ndgp.ices.wg.wgrdbesgov/Input/HCE_2023_10_03_152759.zip")
CE<-CE$CE

CE_DF <- as.data.frame(CE)

CL <- createRDBESDataObject("../../../1. NDGP/ndgp.ices.wg.wgrdbesgov/Input/HCL_2023_10_03_152130.zip")
CL<-CL$CL

CL_DF <- as.data.frame(CL)

#Read the rectangle list from the repository 
url <- "https://github.com/ices-tools-dev/RDBES/raw/master/QC-scripts/RectangleList/ICESRectAreas.csv"
ICESrect <- read.csv(url, header = TRUE)
```

```{r functions, include = FALSE}
catHeader <- function(text = "", level = 3) {
  cat(paste0("\n\n", 
             paste(rep("#", level), collapse = ""), 
             " ", text, "\n"))
}


geom_ices_squares <- function (xlim = c(-49,70), ylim = c(36, 85.5),...){
  outside <- F
  if(xlim[1] < -49) {xlim[1] <- -49; outside <- T}
  if(xlim[2] > 70)  {xlim[2] <- 70; outside <- T}
  if(ylim[1] < -49) {ylim[1] <- -49; outside <- T}
  if(ylim[2] > 85.5){ylim[2] <- 85.5; outside <- T}
  if(outside) print("longitude & latitude must be inside the interval [-49;70] & [36;85.5]")
  list(
    geom_vline(xintercept = -49:70,,...),
    geom_hline(yintercept = seq(36,85.5, by = 0.5),...),
    scale_x_continuous(sec.axis = sec_axis(~.x,
                                           breaks = -49.5:69.5,
                                           labels = paste(rep(LETTERS[1:12],each=10),0:9,sep=''),
                                           guide = guide_axis(check.overlap = TRUE))),
    scale_y_continuous(sec.axis = sec_axis(~.x,
                                           breaks = seq(36.25, 85.25, by = 0.5),
                                           labels = sprintf("%02d",c(1:99)),
                                           guide = guide_axis(check.overlap = TRUE))),
    coord_quickmap(xlim, ylim)  )}

```

```{r, include = FALSE}
# Find top 10 metiers according to the fishing days
top20_metiers_fd <- CE_DF %>%
  group_by(CEmetier6) %>%
  summarise(ofdTot=sum(CEoffFishDay)) %>%
  arrange(desc(ofdTot)) %>%
  top_n(20)
top20_metiers_fd$Top20metiers <- "X"
CE_DF <- left_join(CE_DF,top20_metiers_fd,by="CEmetier6")
CE_DF$topMetiers <- ifelse(is.na(CE_DF$Top20metiers),"OTH",CE_DF$CEmetier6)

# Find top 20 metiers according to the landed value
top20_metiers_lv <- CL_DF %>%
  group_by(CLmetier6) %>%
  summarise(lvTot=sum(as.numeric(CLtotOffLanVal))) %>%
  arrange(desc(lvTot)) %>%
  top_n(20)
top20_metiers_lv$Top20metiers <- "X"
CL_DF <- left_join(CL_DF,top20_metiers_lv,by="CLmetier6")
CL_DF$topMetiers <- ifelse(is.na(CL_DF$Top20metiers),"OTH",CL_DF$CLmetier6)

```

## ICES rectangles and FAO Areas

### CE 

Area and ICES rectangle in the CE data (CEArea, CEstatRect) set is compared with area/rectangle relationship ICES reference list. 
The expected area related to the ICES rectangle is found in the column ICESAreaWithRectangle.
Note that -9 is allowed as unknown ICES rectangle.

```{r echo=FALSE, message=FALSE, warning = FALSE, results='asis'}
ICESrect$sq_check <- "correct"

CE_sq <- CE_DF
CE_sq <- CE_sq[CE_sq$CEstatRect != "-9",]
CE_sq$t <- 1

CE_sq1 <- CE_sq %>%
  group_by(CEvesFlagCou, CEstatRect, CEArea) %>%
  summarise(t=sum(t))


CE_sq2 <- CE_sq1 %>% 
  left_join(ICESrect, by= c("CEArea" = "Area", "CEstatRect"="ICESNAME")) %>%
  select(-Area_27)

CE_sq3 <- CE_sq2[is.na(CE_sq2$sq_check),]

CE_sq4 <- subset(CE_sq3, select=c(CEvesFlagCou, CEstatRect, CEArea))

CE_sq5<- CE_sq4 %>% 
  left_join(ICESrect[c("ICESNAME","Area")], by = c("CEstatRect"="ICESNAME"))%>% 
  distinct(CEvesFlagCou, CEstatRect, .keep_all = TRUE)%>% 
  rename("ICESAreaWithRectangle" = Area)
  
    cat("\n")
    cat("\n")
    cat("<b>Overview of CE data with wrong/unexpected CEArea</b>\n\n")

DT::datatable(CE_sq5, filter = 'top')    

    cat("\n")
    cat("\n")
    cat("<b>CEid's with wrong/unexpected CEArea</b>\n\n")
    cat("Based on the previous identified rectangles, an overview of all CEid for which the CEArea has been identified to not match with the corresponding area in the ICES reference list.\n\n")
    
CE_DF_wrong_areas <- data.frame()

for (i in 1:nrow(CE_sq5)) {
  filtered_data <- CE_DF %>%
    filter(CEvesFlagCou == CE_sq5$CEvesFlagCou[i] & 
           CEstatRect == CE_sq5$CEstatRect[i] & 
           CEArea == CE_sq5$CEArea[i]) %>%
    select(CEid, CEvesFlagCou, CEyear, CEMonth, CEstatRect, CEArea, CEmetier6, CEvesLenCat, CEencrypVesIds)
  
  CE_DF_wrong_areas <- bind_rows(CE_DF_wrong_areas, filtered_data)
}

DT::datatable(CE_DF_wrong_areas, filter = 'top')
```

### CL

Area and ICES rectangle in the CE data (CLArea, CLstatRect) set is compared with area/rectangle relationship ICES reference list. 
The expected area related to the ICES rectangle is found in the column ICESAreaWithRectangle.
Note that -9 is allowed as unknown ICES rectangle.

```{r echo=FALSE, message=FALSE, warning = FALSE, results='asis'}
ICESrect$sq_check <- "correct"

CL_sq <- CL_DF
CL_sq <- CL_sq[CL_sq$CLstatRect != "-9",]
CL_sq$t <- 1

CL_sq1 <- CL_sq %>%
  group_by(CLvesFlagCou, CLstatRect, CLarea) %>%
  summarise(t=sum(t))


CL_sq2 <- CL_sq1 %>% 
  left_join(ICESrect, by= c("CLarea" = "Area", "CLstatRect"="ICESNAME")) %>%
  select(-Area_27)

CL_sq3 <- CL_sq2[is.na(CL_sq2$sq_check),]

CL_sq4 <- subset(CL_sq3, select=c(CLvesFlagCou, CLstatRect, CLarea))

CL_sq5<- CL_sq4 %>% 
  left_join(ICESrect[c("ICESNAME","Area")], by = c("CLstatRect"="ICESNAME"))%>% 
  distinct(CLvesFlagCou, CLstatRect, .keep_all = TRUE)%>% 
  rename("ICESAreaWithRectangle" = Area)
  
    cat("\n")
    cat("\n")
    cat("<b>Overview of CL data with wrong/unexpected CLarea</b>\n\n")

    DT::datatable(CL_sq5, filter = 'top')   

    cat("\n")
    cat("\n")
    cat("<b>CLid's with wrong/unexpected CLarea</b>\n\n")
    cat("Based on the previous identified rectangles, an overview of all CLid for which the CLArea has been identified to not match with the corresponding area in the ICES reference list.\n\n")
    
CL_DF_wrong_areas <- data.frame()

for (i in 1:nrow(CL_sq5)) {
  filtered_data <- CL_DF %>%
    filter(CLvesFlagCou == CL_sq5$CLvesFlagCou[i] & 
           CLstatRect == CL_sq5$CLstatRect[i] & 
           CLarea == CL_sq5$CLarea[i]) %>%
    select(CLid, CLvesFlagCou, CLyear, CLmonth, CLstatRect, CLarea, CLmetier6, CLvesLenCat, CLencrypVesIds)
  
  CL_DF_wrong_areas <- bind_rows(CL_DF_wrong_areas, filtered_data)
}

DT::datatable(CL_DF_wrong_areas, filter = 'top')

```

## ICES rectangle centroids (CL and CE) {.tabset}

CE and CL data points are plotted to the ICES rectangle centroids. A map third map, shows CL data points for which no corresponding CE data points has been submitted. Note that -9 is allowed as unknown ICES rectangle and therefore could lead to such discrepancy between CL and CE spatial data.

```{r  mapCE, include = FALSE,  echo=FALSE, message=FALSE, warning = FALSE}
# Load world data
world <- ne_countries(scale = "medium", returnclass = "sf")
world <- st_set_crs(world, 4326)

# Create empty lists to store plots and filtered CL data
map_combined <- list()
CL_without_CE <- list()

# Iterate over unique countries
unique_countries <- unique(CE_DF$CEvesFlagCou)

for(country in sort(unique_countries)){
  
  # Filter CE and CL data for the current country
  CE_subset_data <- CE_DF %>%
    filter(CEvesFlagCou == country, CEstatRect != '-9') %>%
    distinct(CEstatRect, CEvesFlagCou, topMetiers) %>%
    mutate(lon = ices.rect(CEstatRect)$lon,
           lat = ices.rect(CEstatRect)$lat)
  
  CL_subset_data <- CL_DF %>%
    filter(CLvesFlagCou == country, CLstatRect != '-9') %>%
    distinct(CLstatRect, CLvesFlagCou, topMetiers) %>%
    mutate(lon = ices.rect(CLstatRect)$lon,
           lat = ices.rect(CLstatRect)$lat)
  
  # Extract min and max longitude and latitude for the current country
  min.lon <- min(CE_subset_data$lon, na.rm = TRUE)
  max.lon <- max(CE_subset_data$lon, na.rm = TRUE)
  min.lat <- min(CE_subset_data$lat, na.rm = TRUE)
  max.lat <- max(CE_subset_data$lat, na.rm = TRUE)
  
  # Create sublist for the current country in CL_without_CE list
  CL_without_CE[[country]] <- list()
  
  # Iterate over unique values of topMetiers for the current country
  for(topMetier in sort(unique(CE_subset_data$topMetiers))){
    
    # Subset CE and CL data for the current topMetier
    CE_subset_data_topMetier <- CE_subset_data %>%
      filter(topMetiers == topMetier)
    
    CL_subset_data_topMetier <- CL_subset_data %>%
      filter(topMetiers == topMetier)
    
    # Filter CL data to only contain cases where CLstatRect are in the CL_only_rectangles
    CL_only_rectangles <- CL_subset_data_topMetier %>%
      anti_join(CE_subset_data_topMetier, by = c("lon", "lat")) %>%
      mutate(label = "CL Only")

    # Store the filtered CL data in the sublist for the current country and gear
    CL_without_CE[[country]][[topMetier]] <- CL_DF %>%
      filter(CLvesFlagCou == country,
             CLstatRect != '-9',
             topMetiers == topMetier) %>% 
      semi_join(CL_only_rectangles, by = c("CLstatRect"))%>%
      select(CLid, CLvesFlagCou, CLyear, CLmonth, CLstatRect, CLmetier6, CLvesLenCat, CLencrypVesIds)%>%
      arrange(CLstatRect)
    
    # Create CE plot for the current topMetier
    CE_plot <- ggplot() +
      theme_bw() +
      geom_ices_squares(xlim = c(min.lon, max.lon), ylim = c(min.lat, max.lat), linetype = "dotted", colour = "grey30", linewidth = 0.1) +
      geom_sf(data = world) +
      geom_point(data = CE_subset_data_topMetier, aes(lon, lat), size = 2, colour = "red") +
      coord_sf(xlim = c(min.lon, max.lon), ylim = c(min.lat, max.lat)) +
      xlab("Longitude") +
      ylab("Latitude") +
      ggtitle("CE")
    
    # Create CL plot for the current topMetier
    CL_plot <- ggplot() +
      theme_bw() +
      geom_ices_squares(xlim = c(min.lon, max.lon), ylim = c(min.lat, max.lat), linetype = "dotted", colour = "grey30", linewidth = 0.1) +
      geom_sf(data = world) +
      geom_point(data = CL_subset_data_topMetier, aes(lon, lat), size = 2, colour = "red") +
      coord_sf(xlim = c(min.lon, max.lon), ylim = c(min.lat, max.lat)) +
      xlab("Longitude") +
      ylab("Latitude") +
      ggtitle("CL")
    
    # Create plot for rectangles with CL data but no CE data
    CL_only_plot <- ggplot() +
      theme_bw() +
      geom_ices_squares(xlim = c(min.lon, max.lon), ylim = c(min.lat, max.lat), linetype = "dotted", colour = "grey30", linewidth = 0.1) +
      geom_sf(data = world) +
      geom_point(data = CL_only_rectangles, aes(lon, lat), size = 2, colour = "red") +
      coord_sf(xlim = c(min.lon, max.lon), ylim = c(min.lat, max.lat)) +
      xlab("Longitude") +
      ylab("Latitude") +
      ggtitle("CL without CE")
    
    # Combine CE, CL, and CL only plots
    combined_plot <- ggarrange(CE_plot, CL_plot, CL_only_plot, nrow = 1, ncol = 3)
    
    # Store the combined plot in a list, organized by country and gear
    map_combined[[country]][[topMetier]] <- combined_plot
  }
}
```

```{r, results = "asis", echo = FALSE, warning = FALSE, fig.height=5, fig.width=15}
# Loop over unique countries
for(country in unique_countries) {
  # Output country tab
  catHeader(paste0(country," {.tabset}"), 3)

  # Loop over gears for the current country
  for(gear in names(map_combined[[country]])) {
    # Output gear tab
    catHeader(gear, 4)
    cat("\n")
    
    # Output map for the current gear and country
    print(map_combined[[country]][[gear]])
    
    cat("\n")
    cat("\n")
    cat("<b>Overview of CL data without CE</b>\n\n")
    cat("The following table shows an overview of all CLid for which no CEid exists (landings without effort).\n\n")
    
    # Output table for the current gear and country using knitr's results='asis'
    kable(CL_without_CE[[country]][[gear]], "html", caption = NULL) %>%
      kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"), full_width = TRUE) %>%
      as.character() %>%
      cat()
  }
}
```
