
# CL & CE 

The following analysis allows to check if landings have corresponding effort. This is done by merging CE and CL data sets using unique keys consisting of the following fields: Vessel flag country, Year, Quarter, Month, Area, Statistical rectangle, Fisheries management unit, GSA subarea, Jurisdiction area, Fishing area category, Fresh water name, Exclusive Economic Zone (EEZ), National fishing activity, Metier 6 fishing activity, Incidential by catch mitigation device, Landing location, Vessel length category, Fishing Technique, Mesh size range, Supra Region, Geographical indicator, Specific conditions to technical measures, Deep Sea Regulation.

## Number of unique keys in CE and CL data sets

```{r}
CEkeyColumns <- c("CErecType","CEvesFlagCou","CEyear","CEquar","CEmonth",
                  "CEarea","CEstatRect","CEfishManUnit","CEgsaSubarea",
                  "CEjurisdArea","CEfishAreaCat","CEfreshWatNam","CEeconZone",
                  "CEnatFishAct","CEmetier6","CEIBmitiDev","CEloc",
                  "CEvesLenCat","CEfishTech","CEmesSizRan","CEsupReg",
                  "CEgeoInd","CEspeConTech","CEdeepSeaReg" )

CLkeyColumns <- c("CLrecType","CLvesFlagCou","CLyear","CLquar","CLmonth",
                  "CLarea","CLstatRect","CLfishManUnit","CLgsaSubarea",
                  "CLjurisdArea","CLfishAreaCat","CLfreshWatNam","CLeconZone",
                  "CLnatFishAct","CLmetier6","CLIBmitiDev","CLloc",
                  "CLvesLenCat","CLfishTech","CLmesSizRan","CLsupReg",
                  "CLgeoInd","CLspeConTech","CLdeepSeaReg")

CEkeys <- CE %>%
  group_by_at(CEkeyColumns) %>% 
  summarise(CESciDaySea = sum(CESciDaySea, na.rm=T),
            CEsciFishDay = sum(CEsciFishDay, na.rm = T))
colnames(CEkeys) <- sub("^CE","",colnames(CEkeys))

CLkeys <- CL %>%
  group_by_at(CLkeyColumns) %>% 
  summarise(CLsciWeight = sum(CLsciWeight, na.rm=T))
colnames(CLkeys) <- sub("^CL","",colnames(CLkeys))

keysSummary <- CEkeys %>% 
  rbind(CLkeys) %>% 
  group_by(vesFlagCou,year,recType) %>% 
  summarise(n=n())

ggplot(keysSummary, aes(year, n, fill = recType)) +
  geom_bar(stat = "identity", position = "dodge") +
  facet_wrap(~vesFlagCou, scales = "free_y")+
  labs(y = "Number of unique keys",
       x = "Year",
       fill = "Record type",
       title = "Comparison of CL and CE unique keys")

```

## Landings without corresponding effort

```{r}

lanWoEffort <- CLkeys %>% 
  anti_join(CEkeys, by = colnames(CEkeys)[2:24])
rmarkdown::paged_table(lanWoEffort)

```

## Tons per fishing day calculated from merged CE and CL data sets.

```{r}
CECL <- CEkeys %>% 
  inner_join(CLkeys, by = colnames(CEkeys)[2:24]) %>% 
  mutate(tonsPerFishingDay = sciWeight / sciFishDay,
         gearType = substr(metier6,1,3))

CECL %>% 
ggplot(aes(gearType, tonsPerFishingDay)) +
  geom_boxplot(outlier.color = "red3") +
  facet_wrap(~vesLenCat, scales = "free")+
  labs(y = "Tons per fishing day",
       x = "Gear type",
       title = "Tons per fishing day by gear and vessel length")

CECL %>% 
  ggplot(aes(vesLenCat, tonsPerFishingDay)) +
  geom_boxplot(outlier.color = "red3") +
  facet_wrap(~gearType, scales = "free")+
  labs(y = "Tons per fishing day",
       x = "Vessel length",
       title = "Tons per fishing day by and vessel length and gear")+
  theme(axis.text.x = element_text(angle = 45, hjust=1))

```


