# CL and CE documentation for filling in template 

```{r ReadData2, echo=FALSE, message=FALSE, warning = FALSE}
CL$CLtotOffLanVal <- as.numeric(CL$CLtotOffLanVal)

```

## Data basis and data source {.tabset} 

### OfficialWeight

```{r OfficialWeight}
# weights by data basis and data source 
CLdb <- CL %>%
  group_by(CLyear, CLdBasSciWeig, CLdSouSciWeig) %>%
  summarise(CLoffWeight = sum(CLoffWeight, na.rm = TRUE))

ggplot(CLdb, aes(CLdBasSciWeig, CLoffWeight, fill = CLdSouSciWeig)) +
  geom_bar(stat = "identity") +
  facet_grid(.~ CLyear, scales = "free") +
  theme_bw() +
  theme(text = element_text(size = 20),
        axis.text.x = element_text(angle = 90, hjust = 1)) +
  ylab("OffWeight") +
  ggtitle("Official weight by year, data basis and data source category")


CLdb %>%
  datatable(caption = "Official weight by year, data basis and data source category" , rownames = FALSE, options = list(dom = 't'))
```

### ScientificWeight

```{r ScientificWeight}
# weights by data basis and data source 
CLdb <- CL %>%
  group_by(CLyear, CLdBasSciWeig, CLdSouSciWeig) %>%
  summarise(CLsciWeight = sum(CLsciWeight, na.rm = TRUE))

ggplot(CLdb, aes(CLdBasSciWeig, CLsciWeight, fill = CLdSouSciWeig)) +
  geom_bar(stat = "identity") +
  facet_grid(.~ CLyear, scales = "free") +
  theme_bw() +
  theme(text = element_text(size = 20),
        axis.text.x = element_text(angle = 90, hjust = 1)) +
  ylab("SciWeight") +
  ggtitle("Scientific weight by year, data basis and data source category")


CLdb %>%
  datatable(caption = "Scientific weight by year, data basis and data source category" , rownames = FALSE, options = list(dom = 't', scrollY = TRUE, pageLength = -1))
```

### LandingValue

```{r LandingValue}
CLdb <- CL %>%
  group_by(CLyear, CLdBasSciWeig, CLdSouLanVal) %>%
  summarise(CLtotOffLanVal = sum(CLtotOffLanVal, na.rm = TRUE))

ggplot(CLdb, aes(CLdBasSciWeig, CLtotOffLanVal, fill = CLdSouLanVal)) +
  geom_bar(stat = "identity") +
  facet_grid(.~ CLyear, scales = "free") +
  theme_bw() +
  theme(text = element_text(size = 20),
        axis.text.x = element_text(angle = 90, hjust = 1)) +
  ylab("LanVal") +
  ggtitle("Landings value weight by year, data basis and data source landings value")


CLdb %>%
  datatable(caption = "Landings value weight by year, data basis and data source landings value" , rownames = FALSE, options = list(dom = 't', scrollY = TRUE, pageLength = -1))
```

### NumberFractionalTrips

```{r NumberFractionalTrips}
CEdb <- CE %>%
  group_by(CEyear, CEdBasSciEff, CEdSouSciEff) %>%
  summarise(CEnumFracTrips = sum(CEnumFracTrips, na.rm = TRUE))

ggplot(CEdb, aes(CEdBasSciEff, CEnumFracTrips, fill = CEdSouSciEff)) +
  geom_bar(stat = "identity") +
  facet_grid(.~ CEyear, scales = "free") +
  theme_bw() +
  theme(text = element_text(size = 20),
        axis.text.x = element_text(angle = 90, hjust = 1)) +
  ylab("NumFractionalTrips") +
  ggtitle("Number of fractional trips by year, data basis and data source")


CEdb %>%
  datatable(caption = "Number of fractional trips by year, data basis and data source" , rownames = FALSE, options = list(dom = 't', scrollY = TRUE, pageLength = -1))
```

### NumberDominantTrips

```{r NumberDominantTrips}
CEdb <- CE %>%
  group_by(CEyear, CEdBasSciEff, CEdSouSciEff) %>%
  summarise(CEnumDomTrip = sum(CEnumDomTrip, na.rm = TRUE))

ggplot(CEdb, aes(CEdBasSciEff, CEnumDomTrip, fill = CEdSouSciEff)) +
  geom_bar(stat = "identity") +
  facet_grid(.~ CEyear, scales = "free") +
  theme_bw() +
  theme(text = element_text(size = 20),
        axis.text.x = element_text(angle = 90, hjust = 1)) +
  ylab("NumDominantTrips") +
  ggtitle("Number of dominant trips by year, data basis and data source")


CEdb %>%
  datatable(caption = "Number of dominant trips by year, data basis and data source" , rownames = FALSE, options = list(dom = 't', scrollY = TRUE, pageLength = -1))
```

### OfficialDaysAtSea

```{r OfficialDaysAtSea}
CEdb <- CE %>%
  group_by(CEyear, CEdBasSciEff, CEdSouSciEff) %>%
  summarise(CEoffDaySea = sum(CEoffDaySea, na.rm = TRUE))

ggplot(CEdb, aes(CEdBasSciEff, CEoffDaySea, fill = CEdSouSciEff)) +
  geom_bar(stat = "identity") +
  facet_grid(.~ CEyear, scales = "free") +
  theme_bw() +
  theme(text = element_text(size = 20),
        axis.text.x = element_text(angle = 90, hjust = 1)) +
  ylab("Official days at sea") +
  ggtitle("Official days at sea by year, data basis and data source")


CEdb %>%
  datatable(caption = "Official days at sea by year, data basis and data source" , rownames = FALSE, options = list(dom = 't', scrollY = TRUE, pageLength = -1))
```

### ScientificDaysAtSea

```{r ScientificDaysAtSea}
CEdb <- CE %>%
  group_by(CEyear, CEdBasSciEff, CEdSouSciEff) %>%
  summarise(CESciDaySea = sum(CESciDaySea, na.rm = TRUE))

ggplot(CEdb, aes(CEdBasSciEff, CESciDaySea, fill = CEdSouSciEff)) +
  geom_bar(stat = "identity") +
  facet_grid(.~ CEyear, scales = "free") +
  theme_bw() +
  theme(text = element_text(size = 20),
        axis.text.x = element_text(angle = 90, hjust = 1)) +
  ylab("Scientific days at sea") +
  ggtitle("Scientific days at sea by year, data basis and data source")


CEdb %>%
  datatable(caption = "Scientific days at sea by year, data basis and data source" , rownames = FALSE, options = list(dom = 't', scrollY = TRUE, pageLength = -1))
```

### OfficialFishingDays

```{r OfficialFishingDays}
CEdb <- CE %>%
  group_by(CEyear, CEdBasSciEff, CEdSouSciEff) %>%
  summarise(CEoffFishDay = sum(CEoffFishDay, na.rm = TRUE))

ggplot(CEdb, aes(CEdBasSciEff, CEoffFishDay, fill = CEdSouSciEff)) +
  geom_bar(stat = "identity") +
  facet_grid(.~ CEyear, scales = "free") +
  theme_bw() +
  theme(text = element_text(size = 20),
        axis.text.x = element_text(angle = 90, hjust = 1)) +
  ylab("Official fishing days") +
  ggtitle("Official fishing days by year, data basis and data source")


CEdb %>%
  datatable(caption = "Official fishing days by year, data basis and data source" , rownames = FALSE, options = list(dom = 't', scrollY = TRUE, pageLength = -1))
```

### ScientificFishingDays

```{r ScientificFishingDays}
CEdb <- CE %>%
  group_by(CEyear, CEdBasSciEff, CEdSouSciEff) %>%
  summarise(CEsciFishDay = sum(CEsciFishDay, na.rm = TRUE))

ggplot(CEdb, aes(CEdBasSciEff, CEsciFishDay, fill = CEdSouSciEff)) +
  geom_bar(stat = "identity") +
  facet_grid(.~ CEyear, scales = "free") +
  theme_bw() +
  theme(text = element_text(size = 20),
        axis.text.x = element_text(angle = 90, hjust = 1)) +
  ylab("Scientific fishing days") +
  ggtitle("Scientific fishing days by year, data basis and data source")


CEdb %>%
  datatable(caption = "Scientific fishing days by year, data basis and data source" , rownames = FALSE, options = list(dom = 't', scrollY = TRUE, pageLength = -1))
```

### OfficialVesselFishingHour

```{r OfficialVesselFishingHour}
CEdb <- CE %>%
  group_by(CEyear, CEdBasSciEff, CEdSouSciEff) %>%
  summarise(CEoffVesFishHour = sum(CEoffVesFishHour, na.rm = TRUE))

ggplot(CEdb, aes(CEdBasSciEff, CEoffVesFishHour, fill = CEdSouSciEff)) +
  geom_bar(stat = "identity") +
  facet_grid(.~ CEyear, scales = "free") +
  theme_bw() +
  theme(text = element_text(size = 20),
        axis.text.x = element_text(angle = 90, hjust = 1)) +
  ylab("Official vessel fishing hour") +
  ggtitle("Official vessel fishing hours by year, data basis and data source")


CEdb %>%
  datatable(caption = "Official vessel fishing hours by year, data basis and data source" , rownames = FALSE, options = list(dom = 't', scrollY = TRUE, pageLength = -1))
```

### ScientificVesselFishingHour

```{r ScientificVesselFishingHour}
CEdb <- CE %>%
  group_by(CEyear, CEdBasSciEff, CEdSouSciEff) %>%
  summarise(CEsciVesFishHour = sum(CEsciVesFishHour, na.rm = TRUE))

ggplot(CEdb, aes(CEdBasSciEff, CEsciVesFishHour, fill = CEdSouSciEff)) +
  geom_bar(stat = "identity") +
  facet_grid(.~ CEyear, scales = "free") +
  theme_bw() +
  theme(text = element_text(size = 20),
        axis.text.x = element_text(angle = 90, hjust = 1)) +
  ylab("Scientific vessel fishing hour") +
  ggtitle("Scientific vessel fishing hours by year, data basis and data source")


CEdb %>%
  datatable(caption = "Scientific vessel fishing hours by year, data basis and data source" , rownames = FALSE, options = list(dom = 't', scrollY = TRUE, pageLength = -1))
```

### OfficialkWDaysAtSea

```{r OfficialkWDaysAtSea}
CEdb <- CE %>%
  group_by(CEyear, CEdBasSciEff, CEdSouSciEff) %>%
  summarise(CEoffkWDaySea = sum(CEoffkWDaySea, na.rm = TRUE))

ggplot(CEdb, aes(CEdBasSciEff, CEoffkWDaySea, fill = CEdSouSciEff)) +
  geom_bar(stat = "identity") +
  facet_grid(.~ CEyear, scales = "free") +
  theme_bw() +
  theme(text = element_text(size = 20),
        axis.text.x = element_text(angle = 90, hjust = 1)) +
  ylab("Official kW Days at sea") +
  ggtitle("Official kW Days at sea by year, data basis and data source")

CEdb %>%
  datatable(caption = "Official kW Days at sea by year, data basis and data source" , rownames = FALSE, options = list(dom = 't', scrollY = TRUE, pageLength = -1))
```

### ScientifickWDaysAtSea

```{r ScientifickWDaysAtSea}
CEdb <- CE %>%
  group_by(CEyear, CEdBasSciEff, CEdSouSciEff) %>%
  summarise(CEscikWDaySea = sum(CEscikWDaySea, na.rm = TRUE))

ggplot(CEdb, aes(CEdBasSciEff, CEscikWDaySea, fill = CEdSouSciEff)) +
  geom_bar(stat = "identity") +
  facet_grid(.~ CEyear, scales = "free") +
  theme_bw() +
  theme(text = element_text(size = 20),
        axis.text.x = element_text(angle = 90, hjust = 1)) +
  ylab("Scientific kW Days at sea") +
  ggtitle("Scientific kW Days at sea by year, data basis and data source")

CEdb %>%
  datatable(caption = "Scientific kW Days at sea by year, data basis and data source" , rownames = FALSE, options = list(dom = 't', scrollY = TRUE, pageLength = -1))
```

### OfficialkWFishingDays

```{r OfficialkWFishingDays}
CEdb <- CE %>%
  group_by(CEyear, CEdBasSciEff, CEdSouSciEff) %>%
  summarise(CEoffkWFishDay = sum(CEoffkWFishDay, na.rm = TRUE))

ggplot(CEdb, aes(CEdBasSciEff, CEoffkWFishDay, fill = CEdSouSciEff)) +
  geom_bar(stat = "identity") +
  facet_grid(.~ CEyear, scales = "free") +
  theme_bw() +
  theme(text = element_text(size = 20),
        axis.text.x = element_text(angle = 90, hjust = 1)) +
  ylab("Official kW Fishing days") +
  ggtitle("Official kW Fishing days by year, data basis and data source")

CEdb %>%
  datatable(caption = "Official kW Fishing days by year, data basis and data source" , rownames = FALSE, options = list(dom = 't', scrollY = TRUE, pageLength = -1))
```

### ScientifickWFishingDays

```{r ScientifickWFishingDays}
CEdb <- CE %>%
  group_by(CEyear, CEdBasSciEff, CEdSouSciEff) %>%
  summarise(CEscikWFishDay = sum(CEscikWFishDay, na.rm = TRUE))

ggplot(CEdb, aes(CEdBasSciEff, CEscikWFishDay, fill = CEdSouSciEff)) +
  geom_bar(stat = "identity") +
  facet_grid(.~ CEyear, scales = "free") +
  theme_bw() +
  theme(text = element_text(size = 20),
        axis.text.x = element_text(angle = 90, hjust = 1)) +
  ylab("Scientific kW Fishing days") +
  ggtitle("Scientific kW Fishing days by year, data basis and data source")

CEdb %>%
  datatable(caption = "Scientific kW Fishing days by year, data basis and data source" , rownames = FALSE, options = list(dom = 't', scrollY = TRUE, pageLength = -1))
```

### OfficialkWFishingHours

```{r OfficialkWFishingHours}
CEdb <- CE %>%
  group_by(CEyear, CEdBasSciEff, CEdSouSciEff) %>%
  summarise(CEoffkWFishHour = sum(CEoffkWFishHour, na.rm = TRUE))

ggplot(CEdb, aes(CEdBasSciEff, CEoffkWFishHour, fill = CEdSouSciEff)) +
  geom_bar(stat = "identity") +
  facet_grid(.~ CEyear, scales = "free") +
  theme_bw() +
  theme(text = element_text(size = 20),
        axis.text.x = element_text(angle = 90, hjust = 1)) +
  ylab("Official kW Fishing hours") +
  ggtitle("Official kW Fishing hours by year, data basis and data source")

CEdb %>%
  datatable(caption = "Official kW Fishing hours by year, data basis and data source" , rownames = FALSE, options = list(dom = 't', scrollY = TRUE, pageLength = -1))
```

### ScientifickWFishingHours

```{r ScientifickWFishingHours}
CEdb <- CE %>%
  group_by(CEyear, CEdBasSciEff, CEdSouSciEff) %>%
  summarise(CEscikWFishHour = sum(CEscikWFishHour, na.rm = TRUE))

ggplot(CEdb, aes(CEdBasSciEff, CEscikWFishHour, fill = CEdSouSciEff)) +
  geom_bar(stat = "identity") +
  facet_grid(.~ CEyear, scales = "free") +
  theme_bw() +
  theme(text = element_text(size = 20),
        axis.text.x = element_text(angle = 90, hjust = 1)) +
  ylab("Scientific kW Fishing hours") +
  ggtitle("Scientific kW Fishing hours by year, data basis and data source")

CEdb %>%
  datatable(caption = "Scientific kW Fishing hours by year, data basis and data source" , rownames = FALSE, options = list(dom = 't', scrollY = TRUE, pageLength = -1))
```

### ScientificGTDaysAtSea

```{r ScientificGTDaysAtSea}
CEdb <- CE %>%
  group_by(CEyear, CEdBasSciEff, CEdSouSciEff) %>%
  summarise(CEgTDaySea = sum(CEgTDaySea, na.rm = TRUE))

ggplot(CEdb, aes(CEdBasSciEff, CEgTDaySea, fill = CEdSouSciEff)) +
  geom_bar(stat = "identity") +
  facet_grid(.~ CEyear, scales = "free") +
  theme_bw() +
  theme(text = element_text(size = 20),
        axis.text.x = element_text(angle = 90, hjust = 1)) +
  ylab("Scientific GT Days at sea") +
  ggtitle("Scientific GT Days at sea by year, data basis and data source")

CEdb %>%
  datatable(caption = "Scientific GT Days at sea by year, data basis and data source" , rownames = FALSE, options = list(dom = 't', scrollY = TRUE, pageLength = -1))
```

### ScientificGTFishingDays

```{r ScientificGTFishingDays}
CEdb <- CE %>%
  group_by(CEyear, CEdBasSciEff, CEdSouSciEff) %>%
  summarise(CEgTFishDay = sum(CEgTFishDay, na.rm = TRUE))

ggplot(CEdb, aes(CEdBasSciEff, CEgTFishDay, fill = CEdSouSciEff)) +
  geom_bar(stat = "identity") +
  facet_grid(.~ CEyear, scales = "free") +
  theme_bw() +
  theme(text = element_text(size = 20),
        axis.text.x = element_text(angle = 90, hjust = 1)) +
  ylab("Scientific GT Fishing days") +
  ggtitle("Scientific GT Fishing days by year, data basis and data source")

CEdb %>%
  datatable(caption = "Scientific GT Fishing days by year, data basis and data source" , rownames = FALSE, options = list(dom = 't', scrollY = TRUE, pageLength = -1))
```

### ScientificGTFishingHours

```{r ScientificGTFishingHours}
CEdb <- CE %>%
  group_by(CEyear, CEdBasSciEff, CEdSouSciEff) %>%
  summarise(CEgTFishHour = sum(CEgTFishHour, na.rm = TRUE))

ggplot(CEdb, aes(CEdBasSciEff, CEgTFishHour, fill = CEdSouSciEff)) +
  geom_bar(stat = "identity") +
  facet_grid(.~ CEyear, scales = "free") +
  theme_bw() +
  theme(text = element_text(size = 20),
        axis.text.x = element_text(angle = 90, hjust = 1)) +
  ylab("Scientific GT Fishing hours") +
  ggtitle("Scientific GT Fishing hours by year, data basis and data source")

CEdb %>%
  datatable(caption = "Scientific GT Fishing hours by year, data basis and data source" , rownames = FALSE, options = list(dom = 't', scrollY = TRUE, pageLength = -1))
```

### OfficialSoakingMeterHour

```{r OfficialSoakingMeterHour}
CEdb <- CE %>%
  group_by(CEyear, CEdBasSciEff, CEdSouSciEff) %>%
  summarise(CEoffSoakMeterHour = sum(CEoffSoakMeterHour, na.rm = TRUE))

ggplot(CEdb, aes(CEdBasSciEff, CEoffSoakMeterHour, fill = CEdSouSciEff)) +
  geom_bar(stat = "identity") +
  facet_grid(.~ CEyear, scales = "free") +
  theme_bw() +
  theme(text = element_text(size = 20),
        axis.text.x = element_text(angle = 90, hjust = 1)) +
  ylab("Official Soaking meter hour") +
  ggtitle("Official Soaking meter hour by year, data basis and data source")

CEdb %>%
  datatable(caption = "Official Soaking meter hour by year, data basis and data source" , rownames = FALSE, options = list(dom = 't', scrollY = TRUE, pageLength = -1))
```

### ScientificSoakingMeterHour

```{r ScientificSoakingMeterHour}
CEdb <- CE %>%
  group_by(CEyear, CEdBasSciEff, CEdSouSciEff) %>%
  summarise(CEsciSoakMeterHour = sum(CEsciSoakMeterHour, na.rm = TRUE))

ggplot(CEdb, aes(CEdBasSciEff, CEsciSoakMeterHour, fill = CEdSouSciEff)) +
  geom_bar(stat = "identity") +
  facet_grid(.~ CEyear, scales = "free") +
  theme_bw() +
  theme(text = element_text(size = 20),
        axis.text.x = element_text(angle = 90, hjust = 1)) +
  ylab("Scientific Soaking meter hour") +
  ggtitle("Scientific Soaking meter hour by year, data basis and data source")

CEdb %>%
  datatable(caption = "Scientific Soaking meter hour by year, data basis and data source" , rownames = FALSE, options = list(dom = 't', scrollY = TRUE, pageLength = -1))
```

### OfficialNumberHaulSets

```{r OfficialNumberHaulSets}
CEdb <- CE %>%
  group_by(CEyear, CEdBasSciEff, CEdSouSciEff) %>%
  summarise(CEoffNumHaulSet = sum(CEoffNumHaulSet, na.rm = TRUE))

ggplot(CEdb, aes(CEdBasSciEff, CEoffNumHaulSet, fill = CEdSouSciEff)) +
  geom_bar(stat = "identity") +
  facet_grid(.~ CEyear, scales = "free") +
  theme_bw() +
  theme(text = element_text(size = 20),
        axis.text.x = element_text(angle = 90, hjust = 1)) +
  ylab("Official Number of hauls/sets") +
  ggtitle("Official Number of hauls/sets by year, data basis and data source")

CEdb %>%
  datatable(caption = "Official Number of hauls/sets by year, data basis and data source" , rownames = FALSE, options = list(dom = 't', scrollY = TRUE, pageLength = -1))
```

### ScientificNumberHaulSets

```{r ScientificNumberHaulSets}
CEdb <- CE %>%
  group_by(CEyear, CEdBasSciEff, CEdSouSciEff) %>%
  summarise(CEsciNumHaulSet = sum(CEsciNumHaulSet, na.rm = TRUE))

ggplot(CEdb, aes(CEdBasSciEff, CEsciNumHaulSet, fill = CEdSouSciEff)) +
  geom_bar(stat = "identity") +
  facet_grid(.~ CEyear, scales = "free") +
  theme_bw() +
  theme(text = element_text(size = 20),
        axis.text.x = element_text(angle = 90, hjust = 1)) +
  ylab("Scientific Number of hauls/sets") +
  ggtitle("Scientific Number of hauls/sets by year, data basis and data source")

CEdb %>%
  datatable(caption = "Scientific Number of hauls/sets by year, data basis and data source" , rownames = FALSE, options = list(dom = 't', scrollY = TRUE, pageLength = -1))
```

### GearDimensions

```{r GearDimensions}
CEdb <- CE %>%
  group_by(CEyear, CEdBasSciEff, CEdSouSciEff) %>%
  summarise(CEgearDim = sum(CEgearDim, na.rm = TRUE))

ggplot(CEdb, aes(CEdBasSciEff, CEgearDim, fill = CEdSouSciEff)) +
  geom_bar(stat = "identity") +
  facet_grid(.~ CEyear, scales = "free") +
  theme_bw() +
  theme(text = element_text(size = 20),
        axis.text.x = element_text(angle = 90, hjust = 1)) +
  ylab("Gear dimensions") +
  ggtitle("Gear dimensions by year, data basis and data source")

CEdb %>%
  datatable(caption = "Gear dimensions by year, data basis and data source" , rownames = FALSE, options = list(dom = 't', scrollY = TRUE, pageLength = -1))
```

## Metier allocation

```{r OffWeightMIS}
CL$OffWeight_MIS <- ifelse(CL$CLmetier6=='MIS_MIS_0_0_0', CL$CLoffWeight, 0)
CL$OffWeight_ALL <- ifelse(CL$CLmetier6=='MIS_MIS_0_0_0', 0 , CL$CLoffWeight)

CLdb <- CL %>%
  group_by(CLyear) %>%
  summarise(OffWeight_MIS = sum(OffWeight_MIS, na.rm = TRUE), OffWeight_ALL = sum(OffWeight_ALL, na.rm = TRUE))

CLdb$pct_MIS <- format(round(CLdb$OffWeight_MIS/(CLdb$OffWeight_MIS + CLdb$OffWeight_ALL), digits=3), nsmall=3)

CLdb %>%
  datatable(caption = "Metier MIS_MIS_0_0_0 by official weight" , rownames = FALSE, options = list(dom = 't', scrollY = TRUE, pageLength = -1))
```

```{r SciWeightMIS}
CL$SciWeight_MIS <- ifelse(CL$CLmetier6=='MIS_MIS_0_0_0', CL$CLsciWeight, 0)
CL$SciWeight_ALL <- ifelse(CL$CLmetier6=='MIS_MIS_0_0_0', 0 , CL$CLsciWeight)

CLdb <- CL %>%
  group_by(CLyear) %>%
  summarise(SciWeight_MIS = sum(SciWeight_MIS, na.rm = TRUE), SciWeight_ALL = sum(SciWeight_ALL, na.rm = TRUE))

CLdb$pct_MIS <- format(round(CLdb$SciWeight_MIS/(CLdb$SciWeight_MIS + CLdb$SciWeight_ALL), digits=3), nsmall=3)

CLdb %>%
  datatable(caption = "Metier MIS_MIS_0_0_0 by scientific weight" , rownames = FALSE, options = list(dom = 't', scrollY = TRUE, pageLength = -1))
```

```{r lanValMIS}
CL$OffLanVal_MIS <- ifelse(CL$CLmetier6=='MIS_MIS_0_0_0', CL$CLtotOffLanVal, 0)
CL$OffLanVal_ALL <- ifelse(CL$CLmetier6=='MIS_MIS_0_0_0', 0 , CL$CLtotOffLanVal)

CLdb <- CL %>%
  group_by(CLyear) %>%
  summarise(OffLanVal_MIS = sum(OffLanVal_MIS, na.rm = TRUE), OffLanVal_ALL = sum(OffLanVal_ALL, na.rm = TRUE))

CLdb$pct_MIS <- format(round( (CLdb$OffLanVal_MIS/(CLdb$OffLanVal_MIS + CLdb$OffLanVal_ALL)*100 ), digits=3), nsmall=3)

CLdb %>%
  datatable(caption = "Metier MIS_MIS_0_0_0 by landings value" , rownames = FALSE, options = list(dom = 't', scrollY = TRUE, pageLength = -1))


```

```{r OffFishingDays}
CE$offFishDay_MIS <- ifelse(CE$CEmetier6=='MIS_MIS_0_0_0', CE$CEoffFishDay, 0)
CE$offFishDay_ALL <- ifelse(CE$CEmetier6=='MIS_MIS_0_0_0', 0 , CE$CEoffFishDay)

CEdb <- CE %>%
  group_by(CEyear) %>%
  summarise(offFishDay_MIS = sum(offFishDay_MIS, na.rm = TRUE), offFishDay_ALL = sum(offFishDay_ALL, na.rm = TRUE))

CEdb$pct_MIS <- format(round( (CEdb$offFishDay_MIS/(CEdb$offFishDay_MIS + CEdb$offFishDay_ALL)*100 ), digits=3), nsmall=3)

CEdb %>%
  datatable(caption = "Metier MIS_MIS_0_0_0 by official fishing days" , rownames = FALSE, options = list(dom = 't', scrollY = TRUE, pageLength = -1))

```

```{r SciFishingDays}
CE$sciFishDay_MIS <- ifelse(CE$CEmetier6=='MIS_MIS_0_0_0', CE$CEsciFishDay, 0)
CE$sciFishDay_ALL <- ifelse(CE$CEmetier6=='MIS_MIS_0_0_0', 0 , CE$CEsciFishDay)

CEdb <- CE %>%
  group_by(CEyear) %>%
  summarise(sciFishDay_MIS = sum(sciFishDay_MIS, na.rm = TRUE), sciFishDay_ALL = sum(sciFishDay_ALL, na.rm = TRUE))

CEdb$pct_MIS <- format(round( (CEdb$sciFishDay_MIS/(CEdb$sciFishDay_MIS + CEdb$sciFishDay_ALL)*100 ), digits=3), nsmall=3)

CEdb %>%
  datatable(caption = "Metier MIS_MIS_0_0_0 by scientific fishing days" , rownames = FALSE, options = list(dom = 't', scrollY = TRUE, pageLength = -1))

```

## Rectangle source {.tabset} 

### OfficialWeightStatRect

```{r OffWeightStatRect}

CLdb <- CL %>%
  group_by(CLyear, CLdatBasStatRect, CLdSoucstatRect) %>%
  summarise(CLoffWeight = sum(CLoffWeight, na.rm = TRUE))

ggplot(CLdb, aes(CLdatBasStatRect, CLoffWeight, fill = CLdSoucstatRect)) +
  geom_bar(stat = "identity") +
  facet_grid(.~ CLyear, scales = "free") +
  theme_bw() +
  theme(text = element_text(size = 20),
        axis.text.x = element_text(angle = 90, hjust = 1)) +
  ylab("OffWeight") +
  ggtitle("Official weight by year, data basis and data source for statistical rectangle")


CLdb %>%
  datatable(caption = "Official weight by year, data basis and data source for statistical rectangle" , rownames = FALSE, options = list(dom = 't', scrollY = TRUE, pageLength = -1))

```

### OfficialWeightStatRect

```{r FDStatRect}

CEdb <- CE %>%
  group_by(CEyear, CEdatBasStatRect, CEsoucStatRect) %>%
  summarise(CEoffFishDay = sum(CEoffFishDay, na.rm = TRUE))

ggplot(CEdb, aes(CEdatBasStatRect, CEoffFishDay, fill = CEsoucStatRect)) +
  geom_bar(stat = "identity") +
  facet_grid(.~ CEyear, scales = "free") +
  theme_bw() +
  theme(text = element_text(size = 20),
        axis.text.x = element_text(angle = 90, hjust = 1)) +
  ylab("OffWeight") +
  ggtitle("Official fishing days by year, data basis and data source for statistical rectangle")



CEdb %>%
  datatable(caption = "Official fishing days by year, data basis and data source for statistical rectangle" , rownames = FALSE, options = list(dom = 't', scrollY = TRUE, pageLength = -1))


```
